# Introduction {-}

<!-- OLD INTRO 
This dissertation explores the role of public pressure campaigns in U.S. federal agency rulemaking, a technocratic policy process where "public participation" is usually limited to sophisticated lobbying but occasionally includes millions of people mobilized by public pressure campaigns. Public comment periods on proposed policies purport to provide democratic accountability. Yet, theories of bureaucratic policymaking largely ignore the occasional bursts of civic engagement that generate the vast majority of public comments on proposed rules. To fill this gap, I build and test theories about the role of public pressure in policymaking. I collect and analyze millions of public comments to develop the first systematic measures of civic engagement and influence in bureaucratic policymaking. -->

This dissertation is about public pressure campaigns that target U.S. federal agency rulemaking, technocratic policy processes where public participation is usually limited to a few policy insiders but that occasionally explode into the most contentious policy conflicts of our time. I examine who organizes public pressure campaigns and why, whether these campaigns affect congressional oversight, and whether they affect policy. Answering these questions informs our understanding of bureaucratic politics and interest group lobbying, organizing, and mobilizing tactics. At a time when the vast majority of federal policy is made in the bureaucracy, the relationship between citizens and government depends on bureaucratic policymaking. If ordinary people have a voice in bureaucratic policymaking, I argue, it is through public pressure campaigns. The capacities required to influence national-level policy are those of organized groups, not individuals acting alone. Thus, understanding the nature and effects of these campaigns is key to understanding modern democracy. 

With the rise of the administrative state, U.S. federal agencies have
become a major site of policymaking and political conflict. By some
estimates, upward of 90% of legally binding U.S. federal policy is now
written by agencies. Agency rules are revised much more frequently than
statutory law [@Wagner2017]. In the years or decades between
legislative enactments, federal agencies make legally binding rules
interpreting and reinterpreting old statutes to address emerging issues
and priorities. 

Examples are striking: Many effects of the Dodd-Frank Wall
Street Reform and Consumer Protection Act were largely unknown until the
specific regulations were written, and U.S. policy on banking continues to change as these
rules are revised. Congress authorizes billions of dollars in grants, subsidies, and
leases for public lands, but who gets these benefits depends on agency policy. In
the decades since the last major environmental legislation, agencies
have written thousands of pages of new environmental regulations and
thousands more changing tack under each new administration. 

Agency rules significantly shape lives and fortunes. For example, in 2006,
citing the authority of statutes last amended in the 1950s, the Justice
Department's Bureau of Prisons proposed a rule restricting eligibility
for parole. In 2016, the Bureau withdrew this rule and announced it
would require fewer contracts with prison companies,
precipitating a 50% loss of industry stock value. Six months later, a
new administration announced these policies would again be reversed,
leading to a 130% increase in industry stock value. Agency clearly rulemaking
matters.

Less clear, however, is how the new centrality of agency rulemaking fits
with democracy. In addition to the bureaucracy's complex relationships with
the president, Congress, and the industries they support and regulate, agencies have complex and poorly understood
relationships with the public and advocacy groups. Relationships with
constituent groups may even provide agency officials with a degree of "autonomy" from their political principals in Congress [@Carpenter2001].

<!-- DEMOCRACY has problems and bureaucratic solutions-->
Bureaucratic organization is a core feature of nearly all ambitious human projects, including modern democracies. 
Bureaucracy---and agency rulemaking in particular---responds to two major challenges faced by large democracies. 
First, large democracies are vulnerable to the fleeting passions of the mass public. To combat this, many decisions are left to unelected experts who, ideally, exercise judgment loosely guided by the public. 
Second, not everyone can vote on every policy decision. We thus delegate power to elected representatives (who then delegate it to deputies), create temporary mini-publics, or solicit input from those most affected or moved by a public decision.^[
    As imagined by @Dahl1989, mini-publics are deliberative and representative bodies of individuals selected at random. Besides juries, however, randomly selected deliberative bodies are rare. Instead, citizens more often engage in government decisions when given opportunities to opt-in, such as hearings, petitions, and public comment periods. These mechanisms of civic engagement generate a different, more contentious flavor of public input than the discourse imagined by scholars who focus on deliberation.] 
Most policy in large democracies is thus made by bureaucrats, supposedly guided indirectly through elected representatives and directly by limited public input. 

While bureaucracies address both problems---they institutionalize expert counterweights to mass politics and make larger volumes of policy than any plebiscite could---they do not resolve them. 
Both problems persist in bureaucratic policymaking. Using bureaucracy to address problems as diverse resisting populism and ensuring representation creates contradictions in the tasks assigned to government officials [@Wilson1989].
Bureaucracies are run by experts who are often embedded in professional networks [@Carpenter2001; @Carpenter2014]. At the same time, officials are deputized by and thus accountable to elected officials. Moreover, many bureaucracies also have procedures that create opportunities for public input.  The result is the famous "Bureaucracy Problem" [@Wilson1967]; it is far from clear how bureaucratic decisions are to balance expertise, accountability to elected officials, and responsiveness to public input in policymaking. 
 

<!--
TODO THE BELOW IS REPEATED FROM WHYMAIL--SORT OUT BOOK FROM WHYMAIL MATERIAL! 
-->

Participatory processes like public comment periods, where government
agencies must solicit public input on draft policies, highlight the tensions of bureaucratic policymaking in a democracy. Comment periods are said to
provide political oversight opportunities [@Balla1998; @McCubbins1984],
democratic legitimacy [@Croley2003; @Rosenbloom2003], and new forms of expertise and technical
information [@Yackee2006JPART; @Nelson2012; @Wagner2010].

Activists, politicians, and the press often discuss comments periods as if they were an inherently majoritarian or pluralist institution. After one particularly controversial policy battle, coverage in the New York Times reporters wrote that "The purpose of the public comment period was to objectively gauge Americans sentiment before changing a policy that could profoundly affect their lives." It is clear that rulemaking profoundly affects lives. The extent to which public comment periods gauge public sentiment is much less clear.  Of the thousands of policies that government institutions make each year, direct public input tends to be limited to only the most contentious policy debates. Even elected officials in positions to oversee bureaucratic policymaking infrequently play any role in bureaucratic policymaking. While recent scholarship on
agency policymaking has shed light on the sophisticated lobbying by
businesses and political insiders [@Yackee2006JOP], we know surprisingly little about the vast majority of public comments, which are submitted by ordinary people
as part of public pressure campaigns.
    
Activists frequently target
agency policymaking with letter-writing campaigns, petitions, protests,
and by mobilizing people to attend hearings, all classic examples of "civic
engagement" [@Verba1987]. As I show in \@ref(why-results), most comments submitted to
    regulations.gov are form letters, more akin to petition signatures than sophisticated lobbying. Indeed, approximately 40 million out of
    50 million (80%) of these public comments were mobilized by just 100
    advocacy organizations.
    Yet civic engagement remains poorly understood
in the context of bureaucratic policymaking.

The occasional bursts of civic engagement in bureaucratic policymaking that public pressure campaigns generate
raise practical and theoretical questions for the practice of
democracy. 
These practical and theoretical questions hinge on unanswered empirical
questions: Who is behind these campaigns? Do they affect policy? If so, by what mechanisms?
Existing research finds that commenters believe their comments matter
[@Yackee2015JPART] and that the number of public comments varies across
agencies and policy processes
[@Moore2017].     
In particular, scholars have found that mass comment campaigns drive
    significant participation of ordinary people in Environmental
    Protection Agency rulemaking
    [@Potter2017; @Balla2018]. @Cuellar2005, examining public input in three rulemaking processes, finds that members of the lay public, not professional policy influencers,
    made up the majority of commenters, demonstrating "demand among the
    mass public for a seat at the table in the regulatory process."  Yet, the relationship
between the scale of public engagement and policy change remains
untested. Indeed, we have much to understand about the causes
and effects of public pressure campaigns before we are in a position to ask if
they are a mechanism for groups to influence policy. Most critically, we
must understand who mobilizes public pressure campaigns and why.

Leading models of influence in bureaucratic policymaking focus on two key political forces: sophisticated interest group lobbying and political constraints from Congress and courts. 
As bureaucrats learn about policy problems and balance interest-group demands, public comment processes allow lobbying organizations to provide useful technical information and inform decision-makers of their preferences on draft policies. 
Agencies may then update policy positions within constraints imposed by their political principals.

While this may describe most cases of bureaucratic policymaking, these models neither explain nor account for the contentious politics that occasionally inspire millions of ordinary people to respond to calls for public input on draft agency policies. Political scientists have largely ignored mass engagement in bureaucratic policymaking, leaving a weak empirical base for normative and prescriptive work. 
Like other forms of mass political participation, such as protests and letter-writing campaigns, 
mass public comments on draft agency rules provide no new technical information. <!--%In this sense, they are not useful. -->
Nor do they wield any formal authority to reward or sanction bureaucrats, as comments from members of Congress might. 
The number on each side, be it ten or ten million, has no legal import for an agency's response. 

<!--
% Policymakers may very well pay no attention to them. 
%Instead, scholars focus on the sophisticated lobbying efforts of powerful interest groups, whose role in shaping policy has been theoretically developed and empirically tested.
% If our models and conventional wisdom is correct, why do
Yet, agencies occasionally receive input from a large number of ordinary people. %Why? 
--> 

How, if at all, should scholars incorporate mass engagement into models of bureaucratic policymaking? 

I take up a part of this question in each of the following chapters. Each draws on different kinds of literature to better understand bureaucratic policymaking. Chapter \@ref(macro) brings in the literature on public opinion and the attention of parties to different issues over time, setting pressure campaigns aside and zooming out to the broadest relationships between mass politics and policy outputs. Chapter \@ref(whymail) brings the focus to specific policy fights, integrating literature on interest-group mobilization and bureaucratic politics to understand why public pressure campaigns target agencies in the first place. Chapter \@ref(influence) focuses squarely on the classic bureaucratic politics question of interest group influence in policymaking but expanded to account for public pressure campaigns. Chapter \@ref(EJ) then zooms out again, this time bringing in the literature on social movement pressure to show that pressure campaigns are more than a lobbying tactic; they are also an institutionalized form of contentious politics. These chapters address the literature on public opinion, party politics, interest groups, lobbying, and social movements in turn.<!--TODO, my review of these literatures in this introduction is brief. My aim is to provide a general foundation.-->

<!-- TODO: intro to pol-sci lit that is too broad for elsewhere? -->

<!--## Rulemaking {-}-->

The theories about the drivers of public participation and the mechanisms by which it may affect policy that I advance and test in the following chapters may apply to many contexts where public pressure is aimed at decision-makers. My empirical terrain, however, is policymaking by U.S. federal agencies, specifically the process of "notice-and-comment" rulemaking prescribed in the Administrative Procedure Act (APA). The APA governs the process by which federal agencies develop and issue legally binding policies. It requires agencies to publish proposed (draft) and final policies (rules) in the Federal Register and provide opportunities for the public to comment on draft rules. The legal requirements of the APA impose a great deal of structure on the politics of rulemaking, making it well-suited for quantitative study @Carpenter2020. At the same time, APA requirements have created an extremely legalistic and technocratic form of discourse, leading scholarship on rulemaking to be dominated by legal scholars.

<!-- > IMPORTANT TODO: General into to scholarship on rulemaking, @Yackee2019, @Potter2016, @PotterShipan2019 -->


<!--TODO SUSAN: "instead of presidents, Congress, and judicial review, add a general section (with, say, 2-4 meaty paragraphs with lots of citations to key works on bureaucratic politics).   This section should explain what we know about the public bureaucracy’s generally – they are hierarchical, technocratic, driven by expertise, have odd political accountability relationships, are not elected, etc. and then introduce rulemaking as one of the most important policy tools of bureaucracies.  Here you should comment on judicial review and how it “matters” to rulemaking.  Your reader needs to know this contextual information to understand how and why mass comments might matter to bureaucratic officials in later chapters." -->

<!-- ### Presidential Agendas and Oversight {-}-->

<!-- > TODO: General overview of the president's role in rulemaking, @Ferejohn1990, @Potter2019  Haeder OIRA, Yackee2006bush-->

<!-- ### Congressional Agendas and Oversight {-}-->

<!-- > TODO: General overview of Congress's role in rulemaking, @McCubbins1984, @McCubbins1987, @Huber2002, @Macdonald, @Feinstein2017, @Lowande2018JOP, @Lowande2017, @Clinton2014AJPS -->

<!-- ### Judicial Review {-}-->

<!-- > TODO: General overview of judicial review, @judgelord2016MPSA, @Ferejohn1990, -->

```{r child = here::here("00-intro-adlaw.md")}
```



## Outline of the book {-}

In Chapters \@ref(whymail)-\@ref(EJ), I develop and test theories about the roles of individuals, organizations, coalitions, and social movements in bureaucratic policymaking. Chapter \@ref(macro) first introduces the scale of policymaking and the types of policies that federal agencies make, examining how patterns in bureaucratic policymaking do and do not align with shifts in the broader political system. Chapter \@ref(policy) concludes with remarks about the implications for my analysis for ongoing debates over potential reforms to the policy process. 

```{r child = here::here("outline.md")}
```

