# Introduction: Why Study Public Participation in Bureaucratic Policymaking


This dissertation is about public pressure campaigns that target U.S. federal agency rulemaking, a technocratic policy process where participation is usually limited to a few policy insiders. Occasionally, however, public pressure campaigns help make agency rules some of the most hotly contested policies of our time. I examine who organizes public pressure campaigns and why, whether these campaigns affect congressional oversight, and whether they affect policy. Answering these questions informs our understanding of bureaucratic politics as well as interest group lobbying, organizing, and mobilizing tactics. At a time when the vast majority of policy is made in bureaucracies, the relationship between citizens and government depends on bureaucratic policymaking. If ordinary people have a voice in bureaucratic policymaking, I argue, it is through public pressure campaigns. The capacities required to influence national-level policy are those of organized groups, not individuals acting alone. Thus, understanding the nature and effects of these campaigns is key to understanding modern democracy. 

With the rise of the administrative state, U.S. federal agencies have become a major site of policymaking and political conflict. By some estimates, upward of 90% of legally binding U.S. federal policy is now written by agencies [@Warren2010]. Agency rules are revised much more frequently than statutory law [@Wagner2017]. In the years or decades between legislative enactments, federal agencies make legally binding rules that interpret and reinterpret old statutes to address emerging issues and priorities. Since @Kerwin1992 observed that "Rulemaking has become the most common and instrumental form of lawmaking" (p. 114), it has only become more true. 

To illustrate the importance of bureaucratic policymaking, one could pick from thousands of examples of how our food, water, medicine, prisons, energy system, and financial system are governed through agency rulemaking. Congress authorizes billions of dollars in grants, subsidies, and leases for public lands, but who gets these benefits depends on agency policy. The effects of the Dodd-Frank Wall Street Reform and Consumer Protection Act were largely unknown until the specific regulations were written, and U.S. policy on banking continues to change as these rules are revised.  In the decades since the last major environmental legislation, agencies have written thousands of pages of new environmental regulations and thousands more, changing tack under each new administration. 

Agency rules significantly shape lives and fortunes. For example, in 2006, citing the authority of statutes last amended in the 1950s, the Justice Department's Bureau of Prisons proposed a rule restricting eligibility for parole. In 2016, the Bureau withdrew this rule and announced it would require fewer contracts with prison companies, precipitating a 50% loss of industry stock value. Six months later, a new administration announced these policies would again be reversed, leading to a 130% increase in industry stock value. Agency rulemaking clearly matters.

Less clear, however, is how the new centrality of agency rulemaking fits with democracy. In addition to the bureaucracy's complex relationships with the president, Congress, and the industries they support and regulate, agencies have complex and poorly understood relationships with the public and with advocacy groups. Relationships with constituent groups may even provide agency officials with a degree of "autonomy" from their political principals in Congress [@Carpenter2001].

<!-- DEMOCRACY has problems and bureaucratic solutions-->
Bureaucratic organization is a core feature of nearly all ambitious human projects, including modern democracies.
Bureaucracy---and bureaucratic policymaking in particular---helps address two major challenges faced by large democracies. First, large democracies are susceptible to the fleeting passions of the mass public. To combat this, many decisions are left to unelected experts who, ideally, exercise judgment loosely guided by the public. 
Second, not everyone can vote on every policy decision. We thus delegate power to elected representatives (who then delegate it to unelected deputies in the bureaucracy), solicit input from those most affected or moved by a public decision, and create temporary mini-publics.^[
    As imagined by @Dahl1989, mini-publics are deliberative and representative bodies of individuals selected at random. Besides juries, however, randomly selected deliberative bodies are rare. Instead, citizens more often engage in government decisions when given opportunities to opt-in, such as hearings, petitions, and public comment periods. These mechanisms of civic engagement generate a different, more contentious flavor of public input than the discourse imagined by scholars who focus on deliberation.] 
Most policy in large democracies is thus made by bureaucrats, supposedly guided indirectly through elected representatives and directly by limited forms of public input. 

While bureaucracies address both of these challenges---they institutionalize expert counterweights to mass politics and make larger volumes of policy than any plebiscite could---they do not resolve them. 
Both challenges are especially acute in bureaucratic policymaking. Using bureaucracy to address challenges as diverse as resisting populism, enabling representative democracy, and encouraging direct participation in policymaking creates contradictions in the tasks assigned to government officials [@Wilson1989]. Bureaucracies are run by experts who are often embedded in professional networks and epistemic communities that value very specific kinds of expertise [@Carpenter2001; @Carpenter2014]. At the same time, officials are deputized by, and are thus accountable to, elected officials. Moreover, bureaucratic policymaking procedures often aim to create opportunities for direct public input, such as public comment periods on draft policies. The result is the apogee of the famous "Bureaucracy Problem" [@Wilson1967]; bureaucracies are expected to optimize multiple conflicting goals, each goal involving different types of relevant information, different constituents, and, often, attracting the attention of different scholars. It is far from clear how bureaucratic decisions are to balance expertise, accountability to elected officials, and responsiveness to public input in policymaking. 
 
<!--
TODO THE BELOW IS REPEATED FROM CH 2--SORT OUT BOOK FROM Ch 2 MATERIAL! 
-->

Participatory processes like public comment periods, where government agencies must solicit public input on draft policies, bring the tensions of bureaucratic policymaking in a democracy into sharp focus. Comment periods are said to provide political oversight opportunities [@Balla1998; @McCubbins1984], democratic legitimacy [@Croley2003; @Rosenbloom2003], and new forms of expertise and technical information [@Yackee2006JPART; @Nelson2012; @Wagner2010].

Activists, politicians, and the press often discuss comment periods as if they are an inherently majoritarian or pluralist institution. After one particularly controversial policy battle, reporters in the New York Times wrote that "[t]he purpose of the public comment period was to objectively gauge Americans’ sentiment before changing a policy that could profoundly affect their lives" [@Lipton2015]. It is clear that rulemaking profoundly affects lives. The extent to which public comment periods gauge public sentiment is much less clear. Of the thousands of policies that government institutions make each year, direct public input tends to be limited to only the most contentious policy debates. Even elected officials who are in positions to oversee bureaucratic policymaking infrequently play any role in bureaucratic policymaking. 
 
<!-- BETTER CONNECT IDEAS IN THIS PARAGRAPH-->

While most federal agency policies receive little public attention, activists occasionally expand the scope of conflict by targeting agency policymaking with letter-writing campaigns, petitions, protests, and by mobilizing people to attend hearings, all classic examples of "civic engagement" [@Verba1987]. As I show in \@ref(why-results), most comments submitted to  regulations.gov are form letters, more akin to petition signatures than sophisticated lobbying. Indeed, approximately 80% of public comments on federal agency rules were mobilized by just 100  advocacy organizations. Yet civic engagement remains poorly understood in the context of bureaucratic policymaking. While recent scholarship on agency policymaking has shed light on the sophisticated lobbying by businesses and political insiders [@Yackee2006JOP], we know surprisingly little about the vast majority of public comments, which are submitted by ordinary people as part of public pressure campaigns.

The occasional bursts of civic engagement in bureaucratic policymaking that public pressure campaigns generate raise practical and theoretical questions for the practice of democracy.  These practical and theoretical questions hinge on unanswered empirical questions: Who is behind these campaigns? Do they affect policy? If so, by what mechanisms?

Existing research finds that commenters believe their comments matter [@Yackee2015JPART] and that the number of public comments varies across agencies and policy processes [@Moore2017]. In particular, scholars have found that mass comment campaigns drive significant participation of the lay public in rulemaking at the Environmental Protection Agency  [@Potter2017; @Balla2018]. @Cuellar2005, examining public input in three rulemaking processes, finds that members of the lay public, not professional policy influencers,  made up the majority of commenters, demonstrating "demand among the  mass public for a seat at the table in the regulatory process." Yet, the relationship between the scale of public engagement and policy change remains untested. Indeed, we have much to understand about the causes and effects of public pressure campaigns before we are in a position to ask if they are a mechanism for groups to influence policy. Most critically, we must understand who mobilizes public pressure campaigns and why.

## What We Know About Bureaucratic Policymaking

Departing from the conventional wisdom that government was necessarily political, an influential movement in public administration in the early twentieth century promoted the idea that challenges of governance could be solved rationally [@Svara1998]---what @Stone2002 calls the "rationality project." Administration was to be a science with objective methods to design and carry out administrative tasks. The principles of good administration were discoverable, generalizable, and neutral [@Long1949; @Caiden1984].

In the mid-twentieth century, a wave of scholarship pushed back, arguing that "the lifeblood of administration is power" and that bureaucratic decision-making is saturated with "forces on whose support, acquiescence, or temporary impotence the power to act depends" [@Long1949, pg. 1]. Rather than merely subordinate cogs in a governmental hierarchy, bureaucrats' decisions are functions of a multitude of relationships with the other political institutions in which they are embedded. "Administrative organizations, however much they may appear to be the creations of art, are institutions produced in history and woven in the web of social relationships that give them life" [@Long1949, pg. 6]. The work of bringing politics back into the study of bureaucracy is an active program [@Yackee2019].

Long suggested that Congress, individual members of Congress, committees, courts, other agencies, presidential advisors, and the president all affect agency policymaking, but the effect of these more official demands "varies with the political strength of the group demand embodied in it" [@Long1949, pg. 7]. That is, the effect of official demands is conditional on the power of the coalition supporting them. In the language of principal-agent theory, the effect of principals on agencies is mediated by their level of political support. Likewise, we might say that the effect of interest groups that attempt to influence bureaucratic policymaking is mediated by their access to formal levers of power. 

Leading models of influence in bureaucratic policymaking focus on two key political forces: sophisticated interest group lobbying and political constraints from Congress and courts. 
As bureaucrats learn about policy problems and balance interest-group demands, public comment processes allow lobbying organizations to provide useful technical information and inform decision-makers of their preferences on draft policies. 
Agencies may then update policy positions within constraints imposed by their political principals. 

The remainder of this subsection offers a brief review of the special institutional context of bureaucratic policymaking, then scholarship on interest group lobbying, then scholarship on principal-agent dynamics, and finally the limited scholarship on public pressure campaigns and the bureaucracy, most of which comes from administrative law scholars. 


### Accountability to the President, Congress, and the Courts

Presidents, Congress, and courts all affect agency policymaking [@Moe1985]. Yet, agencies vary in their independence from presidential and congressional agendas [@Carpenter2001; @Selin2015].
As a result, agencies vary in their responsiveness to Congress [@Clinton2014AJPS; @Farhang2015], the courts [@Lauderdale2012; @Carrigan2019], the president [@Carrigan2021], and public opinion [@Dunleavy1991]. 

Principal-agent models, where political actors use various rewards and sanctions to affect agency behavior, offer one way to think about accountability. Stemming from the image of a hierarchy of governmental authority, models of principal-agent dynamics focus on how institutional design and incentives can increase political control over administrative institutions. Specifically, these models focus on how Congress and the president delegate authority and then attempt to constrain bureaucrats' exercise of those authorities. For example, models of delegation suggest that rational principals will delegate to agents with similar goals, repeated interactions, and when they are able to overcome commitment and information problems [@Bendor2001]. Mechanisms of congressional control over the bureaucracy include congressional oversight and administrative procedures that require agencies to be transparent and give interest groups opportunities to raise concerns [@McCubbins1987]. 

While early principal-agent scholarship focused on either Congress or the president [@Wildavsky1964; @Niskanen1975], newer models of bureaucratic policymaking recognize that agency actions are simultaneously constrained by multiple other branches of government [@Moe1985; @Potter2016]. Models of political oversight also now appreciate the role of interest groups in shaping interactions among branches [@McCubbins1984; @McCubbins1987]. I take up the role of interest groups in congressional oversight of bureaucratic policymaking in \@ref(oversight-theory).

<!-- PRESIDENT --> 

Agency rulemaking is where the rubber hits the road for both legislation and presidential agendas [Huber2002; @Devins2008; @Yackee2009bush; @Kerwin2018].
While Congress intentionally designs agencies with varying levels of presidential control [@Lewis2014; @Selin2015], presidential agendas are one of the main drivers of bureaucratic policymaking [@Clinton2014AJPS]. 
Indeed, bureaucratic policymaking varies even more from president to president than the use of direct mechanisms of control would suggest [@Yackee2009bush]. As I show in \@ref(why-results), different presidents inspire different politics in bureaucratic policymaking. Specifically, because the organizations that mobilize public pressure are more aligned with the policy positions of the Democratic party, public pressure campaigns were largely supportive of policies made by the Obama administration and hostile to policies made by the Trump administration.

Presidents---working through the White House Office of Information and Regulatory Affairs (OIRA)---review agency policies and often direct agencies to modify proposed policies [@Haeder2018]. While scholarly attention to OIRA has focused on cost-benefit analysis, @Shapiro2005ELR finds that the president's political priorities tend to trump cost-benefit analysis. OIRA review of agency policies is thus another way that political forces affect agency rules. OIRA review can be influenced by interest groups [@Haeder2015]. To the extent that public pressure campaigns draw the attention of the White House to agency rulemaking, they may affect OIRA review as well. While I do not explicitly address the role of OIRA in rulemaking in this dissertation, my argument that pressure campaigns expand the scope of conflict includes the involvement of additional actors, including the president and OIRA. 

<!--CONGRESS-->

After the president's policy agenda, partisan control of Congress is one of the most important political constraints [@Yackee2009RegGov], especially when Congress is making policy [@West2013] or when agencies fear that a hostile Congress will override their policy decisions [@Potter2016]. Under a divided government, Congress tends to empower agencies that are more independent from the president [@Epstein1999]. We may think of agency policymaking as consistently affected by presidential agendas, with Congress providing shocks and constraints. 

The priorities and attention of Congress and the president affect the volume of rules produced by each agency [@PotterShipan2019]. For example, agencies adjust the number of rules they produce in response to partisan control. Divided government leads to agencies issuing fewer rules and fewer substantively significant rules than they do during periods of unified government [@Yackee2009RegGov]. One reason we see fewer rules under divided government is that agencies strategically time their policy processes to avoid hostile majorities in Congress and the Court [@Potter2017].

While Congress is often modeled as a unitary actor, either enabling or constraining presidential agendas, individual members of Congress also engage the bureaucracy independently [@Lowande2017]. For example, legislators engage in bureaucratic policymaking when they are unable to advance their priorities through legislation due to partisan pressures and chamber control [@Ritchie2017]. Congressional attention to the bureaucracy is also driven by the constituents they represent [@LowandeRitchieLauterbach2018;@Snyder2020], their campaign donors [@Powell2020], and the capacity of their office---for example, oversight committee positions and staff resources [@Judge-Lord2018APSA]. When they do engage in bureaucratic policymaking, Legislators often use the highly institutionalized nature of agency rulemaking to their advantage by raising process concerns about agency policies they dislike [@Lowande2021]. I build on this literature in \@ref(oversight-theory) and show that public pressure campaigns are another reason why members of Congress engage in bureaucratic policymaking. Moreover, I show that the lobbying coalitions that members of Congress support are more likely to achieve their desired policy outcomes. 

<!-- COURTS -->

Courts arbitrate between congressional and presidential control by reviewing bureaucratic policy for congressional intent and adding additional procedural requirements to policymaking [BuenodeMesquita2007]. Because statutes often give interest groups standing to take agency policies to court, judicial review is also a lever for interest group influence. Unlike lawsuits challenging the constitutionality of a statute passed by Congress, lawsuits challenging agency policies often accuse the agency of failing to meet procedural requirements. 

<!-- REORGANIZE THESE TWO PARAGRAPHS--> 

While judges may often uphold or strike down agency policies based on their ideological position [@Cohen1996; @Segal2002; @Bailey2008], the process by which agencies make policy also affects judicial review [@judgelord2016MPSA]. Judges may evaluate an agency's accountability to political principals, the expertise agency officials employed, or by who participated in the policy process. For example, in a landmark case on judicial review, *Chevron U.S.A., Inc. v. NRDC* (2001), the Supreme Court held that the EPA deserved deference because "the regulatory scheme is technical and complex, the agency considered the matter in a detailed and reasoned fashion, and the decision involves reconciling conflicting policies." This suggests that both the agency's use of expertise and the process by which the decision was made affect judicial review. In another landmark case, *U.S. v. Mead Corp.* (2001), the Supreme Court held that courts should review agency policy for "the fairness and deliberation that should underlie a pronouncement of such force." Reviewing courts often cite levels of public participation as evidence of a fair and legitimate process. Opinions frequently note whether or not a policy resulted from notice-and-comment rulemaking and, occasionally, how representative commenters were. For example, in another landmark case on judicial review,  *Vermont Yankee v. NRDC* (1978), Justice Rehnquist noted that "[m]ore than 40 individuals and organizations representing a wide variety of interests submitted written comments."

The features that shape bureaucratic policymaking---attention from political principals, the weight of expertise, and levels of public participation---may shape judicial review as well. 
In addition to accountability and expertise, the level and type of public participation are important criteria for legitimacy from pluralist and direct democracy perspectives [@Woods2013]. In these perspectives, the type of groups or the number of individuals participating in bureaucratic policy may affect the perceived legitimacy of policies. Justices may respond to cues that reflect the relative support of the public or of those affected by the policy [@Clark2009]. While there is little evidence that judges are persuaded by (or even know) the share of public comments supporting a rule, there is evidence that bureaucratic policies with more public participation are more likely to be upheld [@judgelord2016MPSA]. If levels of public attention and participation affect judicial review, we would expect them to also affect the politics of bureaucratic policymaking in the shadow of judicial review. 

This subsection has focused on accountability to political principals. The subsection next reviews the importance of expertise, and, of course, my project squarely addresses who participated. 


### The Institutional Context of Bureaucratic Policymaking

Two features set bureaucratic policymaking apart from how policy is made in Congress, the White House, and courts: it is highly structured and often places much greater weight on specialized expertise.
The importance of structure and expertise are key features of bureaucracy in general, especially large public bureaucracies like the U.S. federal government. 
But structure and expertise take on special significance in the context of policymaking. 
The next two subsections address the special importance of structure and expertise in bureaucratic policymaking. In policymaking, the tasks prescribed by bureaucratic structure are the tasks of lawmaking, including processes for soliciting and responding to public input.
The value placed on expertise makes bureaucratic policymaking notably technocratic. 

#### Structured Policymaking

The theories about the drivers of public participation and the mechanisms by which it may affect policy that I advance and test in the following chapters may apply to many contexts where public pressure is aimed at decision-makers. My empirical terrain, however, is policymaking by U.S. federal agencies, specifically the process of "notice-and-comment" rulemaking prescribed in the Administrative Procedure Act (APA). These policies (federal agency rules) and their potential to change are the contexts for the political dynamics that I explore in Chapter \@ref(whymail) and the dependent variable for Chapters \@ref(influence) and \@ref(ej). The APA governs the process by which federal agencies develop and issue legally binding policies. It requires agencies to publish proposed (draft) and final policies (rules) in the Federal Register and provide opportunities for the public to comment on draft rules. 

The legal requirements of Section 553 of the APA impose a great deal of structure on the politics of rulemaking, making it well-suited for quantitative study [@Carpenter2020]. Agencies must publish draft rules and solicit public comments, which are entered into the public record (unless they contain proprietary information). Both draft and final rules generally include a preamble detailing the agency's authority and reasoning in addition to specific modifications to the U.S. Code. Indeed draft rules are often fully formed policy documents [@West2005; @Yackee2012]. This allows researchers to assess changes between draft and final rules (as I do in Chapters \@ref(influence) and \@ref(ej)). 

After the end of the comment period, the agency usually publishes a Final Rule, which carries the force of law, similar to legislative statutes. The process of publishing a draft rule includes responding to any substantive comments received on the rule. There is no legal requirement that the agency changes the final rule in response to comments, and rules are often unchanged from their draft [@Kerwin2011]. As @Yackee2019 puts it, "current law provides the public the right to participate in---but not the right to influence---rulemaking" (p. 40). 
<!-- TODO  A NEW PARAGRAPH HERE -->
However, accusations that an agency failed to address relevant comments are frequently the ground for lawsuits challenging rules as arbitrary---that is, lacking legal authority because they failed to adhere to technocratic rationality prescribed by the APA and subsequent court decisions interpreting it. 

At the same time, APA requirements have created an extremely legalistic and technocratic form of discourse, leading agency policymaking to be dominated by lawyers and scholarship on rulemaking to be dominated by legal scholars.

<!--
Yet contrary to claims that agency policymaking is “ossified,” @Yackee2010JPART find that procedural constraints aimed at accountability and characterizing muddling through [@Lindblom1959] may actually speed up the promulgation of rules.
-->

<!--EXPERTISE-->
#### Expertise as a Basis of Authority

With hundreds of specialized agencies staffed by career specialists, the U.S. federal bureaucracy has expertise that the legislative branch (in its current form) can only approach by borrowing career agency officials to help write legislation [@Mills2016]. Congress often delegates authority to agencies because of their particular expertise [@Weingast1984; @Bawn1995; Epstein1994; @Huber2002; @Carpenter2012].


A reputation for expertise can increase agencies’ autonomy and power and thus the legitimacy
of their policies (Carpenter 2001).
Agencies almost always appeal to scientific authority to give policies legitimacy. Indeed, reviewing courts often require that policies are justified based on expertise rather than politics. Courts are more likely to defer to policy decisions made by agency officials with more expertise [@Epstein1994].

In part because of its normative power, technical jargon may be employed strategically to avoid oversight and reduce public participation [@Potter2019].
Agencies vary significantly in the levels of formal expertise they employ [@Clinton2008]. Agencies that employ lower levels of formal expertise have higher levels of public participation in their policymaking processes, possibly because these policies are more accessible [@Moore2017].

### Interest Groups Lobbying

<!--For decades, interest groups scholars focused on whether interest groups had "captured" various government agencies. Capture could mean many things, from reducing compliance with demands of the White House or Congress to failing to promote competition.--> 

Because certain kinds of expertise are so highly valued---legally, politically, and culturally---in bureaucratic policymaking, interest groups that are able to provide sophisticated comments on draft policies enjoy a privileged status. Lobbying the bureaucracy often means hiring scientists and lawyers. Well-resourced lobbying efforts, especially businesses, have a particular advantage [@Yackee2006JOP]. 
While there is a vast scholarship on industries and other interest groups "capturing" government institutions, scholars of bureaucratic policymaking have shifted to the more flexible concept of interest group influence [@Yackee2013capture], recognizing that "capture" is often applied unevenly [@Yackee2021].

Although business interests participate at a
higher rate and are more influential than public interest groups [@Yackee2006JOP], agencies do not always accommodate business groups [@Walters2019a]. When the threat of electoral accountability is greater, agencies may be more likely to serve the interests of the public, even if they impose costs on industry [@Miller2018].


Interest groups play a key role in an agency's ability to make policy. Agencies secure independent political power and thus autonomy by forming symbiotic relationships with constituent groups [@Carpenter2001; @Carpenter2014]. Interest group pressure can give agency officials political support and cover from political opposition and thus affect bureaucratic policymaking. Networks of interest groups and agencies not only resist influence from the president and Congress but reform the systems of formal and informal authority governing agency policymaking [@Rhodes1996]. 

Because each agency is embedded in unique issue networks and advocacy coalitions, the politics of bureaucratic policymaking takes different forms at each. For example, agencies vary significantly in the scope and scale of stakeholder involvement in their policy processes [@Yackee2006JOP; @Moore2017]. Indeed, as I show in chapter \@ref(whymail), some agencies face vastly disproportionate levels of public pressure. Agencies cultures and issue networks also lead to distinct ideological biases [@Richardson2017]. In Chapter \@ref(ej), I show that agencies have different levels of receptivity to groups raising distributive justice concerns. 

<!-- GAP -->


### Public Pressure in Bureaucratic Policymaking

Despite our increasingly robust understanding of interest group lobbying and pressure in bureaucratic policymaking, scholars have yet to articulate a role for "outside" lobbying strategies like public pressure campaigns. 
Existing theories neither explain nor account for the contentious politics that occasionally inspire millions of people to respond to calls for public input on draft agency policies. 
Like other forms of mass political participation, such as protests and letter-writing campaigns, mass public comments on draft agency rules provide no new technical information. Nor do they wield any formal authority to reward or sanction bureaucrats, as comments from members of Congress might. 
The number on each side, be it ten or ten million, has no legal import for an agency's response. Given their lack of both technical information and formal authority, political scientists largely dismiss public pressure campaigns as epiphenomenal to interest group bargaining and principal-agent constraints. As a result, normative and prescriptive debates over the role of mass public engagement in bureaucratic policymaking have little empirical evidence to draw upon.

Political science scholarship on public pressure campaigns targeting the bureaucracy is extremely limited. Early scholarship on the topic suggested that form letters differ from other comments [@Schlosberg2007] and suggested that mass comments may be related to longer rulemaking processes [@Shapiro2008]. A recent wave of scholarship has shown that agencies that use high
levels of expertise receive fewer comments [@Moore2017] and that form comments are less likely to be cited by agencies and are less associated with policy change than sophisticated comments [@Balla2020]. Additionally, several studies describe mass comment campaigns at the Environmental Protection Agency [@Potter2017; @Balla2018]. Small adjacent literatures in Information Technology and Public Administration journals document fraud in the public comment process [@Rinfret2021] and the training that bureaucrats receive [@Rinfret2019]. 
I discuss each of these studies more extensively as they relate to each of the following empirical chapters, most extensively in Section \@ref(why-mass).


```{r child = here::here("00-intro-adlaw.md")}
```


## Outline of the Dissertation 

How, if at all, should scholars incorporate mass engagement into models of bureaucratic policymaking? 

I take up a part of this question in each of the following chapters. 
In Chapters \@ref(whymail)-\@ref(ej), I develop and test theories about the roles of individuals, organizations, coalitions, and social movements in bureaucratic policymaking. Chapter \@ref(policy) concludes with remarks about the implications for my analysis for ongoing debates over potential reforms to the policy process. 

Each chapter draws on different kinds of literature to better understand bureaucratic policymaking. <!--I address the literature on interest groups, lobbying, and social movements. -->
Chapter \@ref(whymail) integrates literature on interest-group mobilization and bureaucratic politics to understand why public pressure campaigns target agencies in the first place. Chapter \@ref(influence) focuses squarely on the classic bureaucratic politics question of interest group influence in policymaking but expanded to account for public pressure campaigns. Chapter \@ref(ej) brings in the literature on social movement pressure to show that pressure campaigns are more than a lobbying tactic; they are also an institutionalized form of contentious politics over the distribution of governmental power. 



```{r child = here::here("outline.md")}
```
