# Introduction: Why Study Public Participation in Bureaucratic Policymaking

<!-- OLD INTRO 
This dissertation explores the role of public pressure campaigns in U.S. federal agency rulemaking, a technocratic policy process where "public participation" is usually limited to sophisticated lobbying but occasionally includes millions of people mobilized by public pressure campaigns. Public comment periods on proposed policies purport to provide democratic accountability. Yet, theories of bureaucratic policymaking largely ignore the occasional bursts of civic engagement that generate the vast majority of public comments on proposed rules. To fill this gap, I build and test theories about the role of public pressure in policymaking. I collect and analyze millions of public comments to develop the first systematic measures of civic engagement and influence in bureaucratic policymaking. -->

This dissertation is about public pressure campaigns that target U.S. federal agency rulemaking, a technocratic policy process where public participation is usually limited to a few policy insiders. Occasionally, however, public pressure campaings help make agency rules some of the most hotly contested policies of our time. I examine who organizes public pressure campaigns and why, whether these campaigns affect congressional oversight, and whether they affect policy. Answering these questions informs our understanding of bureaucratic politics as well as interest group lobbying, organizing, and mobilizing tactics. At a time when the vast majority of policy is made in bureaucracies, the relationship between citizens and government depends on bureaucratic policymaking. If ordinary people have a voice in bureaucratic policymaking, I argue, it is through public pressure campaigns. The capacities required to influence national-level policy are those of organized groups, not individuals acting alone. Thus, understanding the nature and effects of these campaigns is key to understanding modern democracy. 

With the rise of the administrative state, U.S. federal agencies have
become a major site of policymaking and political conflict. By some
estimates, upward of 90% of legally binding U.S. federal policy is now
written by agencies [Warren2010]. Agency rules are revised much more frequently than
statutory law [@Wagner2017]. In the years or decades between
legislative enactments, federal agencies make legally binding rules
interpreting and reinterpreting old statutes to address emerging issues
and priorities. Since @Kerwin1992 observed that "Rulemaking has become the most common and instrumental form of lawmaking" (p. 114), it has only become more true. 

To illustrate the point, one could pick from thousands of examples how how agency rulemaking governs our food, water, medicin, prisons, energy system, and financial system. The effects of the Dodd-Frank Wall
Street Reform and Consumer Protection Act were largely unknown until the
specific regulations were written, and U.S. policy on banking continues to change as these
rules are revised. Congress authorizes billions of dollars in grants, subsidies, and
leases for public lands, but who gets these benefits depends on agency policy. In
the decades since the last major environmental legislation, agencies
have written thousands of pages of new environmental regulations and
thousands more changing tack under each new administration. 

Agency rules significantly shape lives and fortunes. For example, in 2006,
citing the authority of statutes last amended in the 1950s, the Justice
Department's Bureau of Prisons proposed a rule restricting eligibility
for parole. In 2016, the Bureau withdrew this rule and announced it
would require fewer contracts with prison companies,
precipitating a 50% loss of industry stock value. Six months later, a
new administration announced these policies would again be reversed,
leading to a 130% increase in industry stock value. Agency rulemaking rulemaking clearly
matters.

Less clear, however, is how the new centrality of agency rulemaking fits
with democracy. In addition to the bureaucracy's complex relationships with
the president, Congress, and the industries they support and regulate, agencies have complex and poorly understood
relationships with the public and advocacy groups. Relationships with
constituent groups may even provide agency officials with a degree of "autonomy" from their political principals in Congress [@Carpenter2001].

<!-- DEMOCRACY has problems and bureaucratic solutions-->
Bureaucratic organization is a core feature of nearly all ambitious human projects, including modern democracies.
Bureaucracy---and bureaucratic policymaking in particular---helps address two major challenges faced by large democracies. 
First, large democracies are susceptible to the fleeting passions of the mass public. To combat this, many decisions are left to unelected experts who, ideally, exercise judgment loosely guided by the public. 
Second, not everyone can vote on every policy decision. We thus delegate power to elected representatives (who then delegate it to deputies), create temporary mini-publics, or solicit input from those most affected or moved by a public decision.^[
    As imagined by @Dahl1989, mini-publics are deliberative and representative bodies of individuals selected at random. Besides juries, however, randomly selected deliberative bodies are rare. Instead, citizens more often engage in government decisions when given opportunities to opt-in, such as hearings, petitions, and public comment periods. These mechanisms of civic engagement generate a different, more contentious flavor of public input than the discourse imagined by scholars who focus on deliberation.] 
Most policy in large democracies is thus made by bureaucrats, supposedly guided indirectly through elected representatives and directly by limited public input. 

While bureaucracies address both challenges to large democracies---they institutionalize expert counterweights to mass politics and make larger volumes of policy than any plebiscite could---they do not resolve them. 
Both challenges are especialy accute in bureaucratic policymaking. Using bureaucracy to address challenges as diverse resisting populism, enabling representative democracy, and encouraging directing public participation creates contradictions in the tasks assigned to government officials [@Wilson1989].
Bureaucracies are run by experts who are often embedded in professional networks [@Carpenter2001; @Carpenter2014]. At the same time, officials are deputized by and thus accountable to elected officials. Moreover, many bureaucracies also have procedures that create opportunities for direct public input, such as public comment periods on draft policies.  The result is the apogee of the famous "Bureaucracy Problem" [@Wilson1967]; that bureaucracies are expected to optimize multiple conflicting goals, each goal the concern of different constituents (and, often, different scholars). It is far from clear how bureaucratic decisions are to balance expertise, accountability to elected officials, and responsiveness to public input in policymaking. 
 

<!--
TODO THE BELOW IS REPEATED FROM WHYMAIL--SORT OUT BOOK FROM WHYMAIL MATERIAL! 
-->

Participatory processes like public comment periods, where government
agencies must solicit public input on draft policies, bring the tensions of bureaucratic policymaking in a democracy into sharp focus. Comment periods are said to
provide political oversight opportunities [@Balla1998; @McCubbins1984],
democratic legitimacy [@Croley2003; @Rosenbloom2003], and new forms of expertise and technical
information [@Yackee2006JPART; @Nelson2012; @Wagner2010].

Activists, politicians, and the press often discuss comments periods as if they are an inherently majoritarian or pluralist institution. After one particularly controversial policy battle, reporters in the New York Times wrote that "The purpose of the public comment period was to objectively gauge Americans sentiment before changing a policy that could profoundly affect their lives" [@Lipton2015]. It is clear that rulemaking profoundly affects lives. The extent to which public comment periods gauge public sentiment is much less clear.  Of the thousands of policies that government institutions make each year, direct public input tends to be limited to only the most contentious policy debates. Even elected officials who are in positions to oversee bureaucratic policymaking infrequently play any role in bureaucratic policymaking. 
    
While most federal agency policies recieve little public attention, activists occasionally expand the scope of conflict by targeting
agency policymaking with letter-writing campaigns, petitions, protests,
and by mobilizing people to attend hearings, all classic examples of "civic
engagement" [@Verba1987]. As I show in \@ref(why-results), most comments submitted to
    regulations.gov are form letters, more akin to petition signatures than sophisticated lobbying. Indeed, approximately 80% of public comments on federal agency rules were mobilized by just 100
    advocacy organizations.
    Yet civic engagement remains poorly understood
in the context of bureaucratic policymaking. While recent scholarship on
agency policymaking has shed light on the sophisticated lobbying by
businesses and political insiders [@Yackee2006JOP], we know surprisingly little about the vast majority of public comments, which are submitted by ordinary people
as part of public pressure campaigns.

The occasional bursts of civic engagement in bureaucratic policymaking that public pressure campaigns generate
raise practical and theoretical questions for the practice of
democracy. 
These practical and theoretical questions hinge on unanswered empirical
questions: Who is behind these campaigns? Do they affect policy? If so, by what mechanisms?


Existing research finds that commenters believe their comments matter
[@Yackee2015JPART] and that the number of public comments varies across
agencies and policy processes
[@Moore2017].     
In particular, scholars have found that mass comment campaigns drive
    significant participation of the lay public in rulemaking at the Environmental
    Protection Agency
    [@Potter2017; @Balla2018]. @Cuellar2005, examining public input in three rulemaking processes, finds that members of the lay public, not professional policy influencers,
    made up the majority of commenters, demonstrating "demand among the
    mass public for a seat at the table in the regulatory process."  Yet, the relationship
between the scale of public engagement and policy change remains
untested. Indeed, we have much to understand about the causes
and effects of public pressure campaigns before we are in a position to ask if
they are a mechanism for groups to influence policy. Most critically, we
must understand who mobilizes public pressure campaigns and why.

## What We Know About Bureaucratic Policymaking

Early studies of public administration in the late nineteenth and early twentieth centuries assumed that problems could be solved rationally. Administration was a science with objective methods to design and carry out administrative tasks. The principles of good administration were discoverable, generalizable, and neutral (@Long1949).

In the mid-twentieth century, a wave of scholarship pushed back, arguing that “the lifeblood of administration is power” and that bureaucratic decision- making is saturated with "forces on whose support, acquiescence, or temporary impotence the power to act depends' [@Long1949, pg. 1]. Rather than merely subordinate cogs in a governmental hierarchy, bureaucrats' decisions are functions of a multitude of relationships with the other political institutions in which they are embedded. 'Administrative organizations, however much they may appear to be the creations of art, are institutions produced in history and woven in the web of social relationships that give them life" [@Long1949, pg. 6].

Long suggested that Congress, individual members of Congress, committees, courts, other agencies, presidential advisors, and the President all affect agency policymaking, but the effect of these more official demands “varies with the political strength of the group demand embodied in it” (Long 1949). That is, the effect of official demands is conditional on the power of the coalition supporting them. That is, the effect of principals on agencies is mediated by their level of political support. Likewise, we might say that the effect of groups is mediated by their access to formal levers of power. 


Leading models of influence in bureaucratic policymaking focus on two key political forces: sophisticated interest group lobbying and political constraints from Congress and courts. 
As bureaucrats learn about policy problems and balance interest-group demands, public comment processes allow lobbying organizations to provide useful technical information and inform decision-makers of their preferences on draft policies. 
Agencies may then update policy positions within constraints imposed by their political principals. The remainder of this subsection offers a breif reviews of the special institutional context of burecratic policymaking, then scholarship on interest group lobbying, then scholarship on principal agent cynamics, and finally the limited scholarship on public pressure campaigns and the burecracy, most of which comes from adminisrative law scholars. 



### Political Principals: The President, Congress, and the Courts

Stemming from the image of a hearchy of governmental authority, models of principal-agent dynamics focus on how  institutional design and incentives can increase political control over administrative institutions. Specifically, these models forcus on how Congress and the president delegate authority and then attempt to constrain bureaucrats' excercise of those authorities. For example, models of delegation suggest that rational principals will delegate to agents with similar goals, repeated interactions, and when they are able to overcome commitment and information problems [@Bendor2001]. Mechanisms of congresssioal control over the bureaucracy include congressional oversight and administrative procedures that require agencies to be transparent and give interest groups opporities to raise concerns [@McCubbins1987]. 

While early principal agent scholarship focued on either Congress or the president [@Wildavsky1964; @Niskanen1975, @McCubbins1984; @McCubbins1987], newer models of bureauratic policymaking recognize that agency actions are simultaniously constrained by multiple other branches of government [@Potter2016].



<!-- PRESIDENT --> 

While Congess intetionally designs agencies with varying levels of presidential control [@Lewis2014;Selin2015], presidental agendas are one of the main drivers of bureaucratic policymaking [@Clinton2014AJPS]. 
Indeed, bureaucratic policymaking varies even more from president to president than the use of direct mechanisms of control would suggest [@Yackee2009bush].

Presidents—working through the Office of Information and Regulatory Affairs (OIRA)— review agency policies and occasionally direct agencies to modify proposed policies [@Haeder2015]. 

<!--CONGRESS-->

After the president's policy agenda, partisan control of Congress is one of the most imporant political constraints [@Yackee2009RegGov], especially when Congress is making policy [@West2013] or when agencies fear that a hostile Congress will override their policy decisions [@Potter2016]. We may think of agency policymaking as consistently affected by presidential agendas, with Congress providing shocks and constraints. The role that parties play in the making of regulations is unclear. Parties may have the greatest effect on agency rules through presidential platforms and agendas [@Yackee2009bush]. 



The priorities and attention of Congress and the president affect the volume of rules produced by each agency [@PotterShipan2019]. . for example agencies adjust the quantity of rules they produce in response to patisan control. Divided government leads to agencies issuing fewer rules and fewer substantively significant rules than they do during periods of unified government [@@Yackee2009RegGov]. One cause of these effects is agencies strategically timing of policymaking to avoid hostile majorities in Congress and the Court [@Potter2017; ]

Members of Congress stratigically engage in bureaucratic policymaking. While Congress is often modeled as a unitary actor either aligned or constraining presidental agendas, individual members of Congress also engage the bureacracy independently [@Lowande2017].
 Legislators engage in bureaucratic plicymaking when they are unable to advance their prirorities through legislation due to partisan pressures and chamber control [@Ritchie2017].  Congressional attention to the bureacuracy is also driven by the constituents they represent [LowandeRitchieLauterbach2018;@Snyder2020], their campaign donors [@Powell2020], and the capacity of their office---for example, oversight committe positions and staff resources [@Judge-Lord2018APSA]. When they do engage in bureacratic policymaking, Legislators often use the highly institutioanlized nature of agency rulemaking to their advantage by raising process concerns about agency policies they dislike [@Lowande2021].

<!-- COURTS -->

Courts also arbitrate between congressional and presidential control by reviewing bureaucratic policy for congressional intent and adding additional procedural requirements to policymaking [BuenodeMesquita2007].

### The Institutional Context of Bureaucratic Policymaking

Two features set bureaucratic policymaking apart from how polcy is made in Congress, the White House, and Courts: it is highly structured and often places much greater weight on specialized expertise.
The importance of structure and expertise are key features of bureacuracy in general, especially large public bureaucrais like the US federal government.  


Structure and expertise take on special significance in the context of policymaking. 
In policymaking the tasks perscripbed by bureacratic struce are the tasks of lawmaking, including processes for soliciting public input.
The value of expertise makes bureacratic policymaking notably techocratic. 

#### Structured Policymaking

The theories about the drivers of public participation and the mechanisms by which it may affect policy that I advance and test in the following chapters may apply to many contexts where public pressure is aimed at decision-makers. My empirical terrain, however, is policymaking by U.S. federal agencies, specifically the process of "notice-and-comment" rulemaking prescribed in the Administrative Procedure Act (APA). The APA governs the process by which federal agencies develop and issue legally binding policies. It requires agencies to publish proposed (draft) and final policies (rules) in the Federal Register and provide opportunities for the public to comment on draft rules. 

The legal requirements of Section 553 the APA impose a great deal of structure on the politics of rulemaking, making it well-suited for quantitative study @Carpenter2020. Agencies must publish draft rules and solicit public comments, which are entered in to the public record (unless they contain propriatry information). Both draft and final rules generally include a preamble detailing the agencies authoirty and reasoning in addition to specific modifications to the US Code. Indeed draft rules are often fully formed policy documents [@West2005; Yackee 2012]. This allows researchers to assess changes between draft and final rules (as I do in Chapters \@ref(influence) and \@ref(ej)). 

After the end of the comment period, the agency usually publishes a Final Rule, which carrys the force of law, similar to legislative statutes.The process of publishing a draft rule includes responding any substantive comments recieved on the rule. There is no legal requriement that the agency change the final rule in response to comments, and rules are often unchanged from their draft [@Kerwin2011]. As @Yackee2019 puts it "current law provides the public the right to participate in---but not the right to influence---rulemaking." 

However, accusations that an agency failed to address relevent comments is frequently the ground for lawsuits challenging rules as arbetrary---that is, lacking legal authority because they failed to adhere to techocratic rationality percribed by the APA and subsiquent court decisions interpreting it. 

At the same time, APA requirements have created an extremely legalistic and technocratic form of discourse, leading scholarship on rulemaking to be dominated by legal scholars.



Agencies vary in their independence from presidential and congressional agendas [@Carpenter2001, @Selin2015]. 

Yet contrary to claims that agency policymaking is “ossified,” Yackee and Yackee (Yackee and Yackee 2010) find that that procedural constraints aimed at accountability and characterizing muddling through [@Lindblom1959] may actually speed up the promulgation of rules.

<!--EXPERTISE-->
#### Expertise as a Basis of Authority

With hundreds of specialized agencies staffed carreer specialists, the U.S. federal bureaucracy has expertise that the legislative branch (in its current form) can only approach by borrowing carreer agency officials to help write legislation [@Mills2016]. Agency expertise is a main reason why Congress delegates authority to agencies [@Weingast1984; @Bawn1995; @Huber2002; @Carpenter2012].



Expertise 

Agencies almost always appeal to scientific authority to give policies legitimacy (indeed courts often seem to require it). Technical jargon may be employed stratigically to avoid oversight and reduce public participation [@Potter2019].

Agencies vary significantly in the levels of formal expertise they employ [@Clinton2008]. Agencies that employ lower levels formal expertise have higher levels of public participation in their policymaking processes, possibly because these policies are more accessable [@Moore2017].

### Interest Groups Lobbying

For decades, intererest groups scholars focused on whether interest groups had "captured" various governement agencies. Capture could mean many things from reducing compliance with demands of the the White House or Congress to failing to promote co. 

Recently, scholars of bureaucrac policymaking have shifted to the more flexible concept of interest group influence [@Yackee2013], recognizing that "capture" is often applied unevenly [@Yackee2021].

Agencies vary in the scope and scale of stakeholder involvement in their policy processes [@Yackee2006JOP, @Moore2017], and their ideological
biases [@Richardson2017].

Although business interests participate at a
higher rate than public interest groups [@Yackee2006JOP], agencies do not always accomidate business groups [@Walters2019a]. When the threat of electoral accountability is greater, agencies may be more likely to serve the interests of the public, even if they impose costs on industry [@Miller2018].

Interest groups play a key role in an agency's ability to make policy. Agencies secure independent political power and thus autonomy by forming symbiotic relationships with constituent groups [@Carpenter2001, @Carpenter2014]. Interest group pressure can give agency officials poltical support and cover from political opposition an thus affect bureauratic policymaking. Networks of interest groups and agencies not only resist influence from the president and congress but reform the systems of formal and informal authorty governing agency policymaking [@Rhodes1996].  

<!-- GAP -->


### Public Pressure

Despite our increasingly robust understanding of interest group lobbying and pressure in bureaucratic policymaking, scholars have yet to articulate a role for "outside" lobbying strategies like public pressure campaigns.  

While this may describe most cases of bureaucratic policymaking, these models neither explain nor account for the contentious politics that occasionally inspire millions of people to respond to calls for public input on draft agency policies. 
Like other forms of mass political participation, such as protests and letter-writing campaigns, 
mass public comments on draft agency rules provide no new technical information. <!--%In this sense, they are not useful. -->
Nor do they wield any formal authority to reward or sanction bureaucrats, as comments from members of Congress might. 
The number on each side, be it ten or ten million, has no legal import for an agency's response. Given their lack of both technical information and formal authority, Political scientists largely dismiss public pressure campaigns as epiphenonmal to interest group bargianing and principal-agent constraints. As a result, normative and prescriptive debates over the role of mass public engagement in buruacratic policymaking have little empirical evidence to draw upon.

<!--
% Policymakers may very well pay no attention to them. 
%Instead, scholars focus on the sophisticated lobbying efforts of powerful interest groups, whose role in shaping policy has been theoretically developed and empirically tested.
% If our models and conventional wisdom is correct, why do
Yet, agencies occasionally receive input from a large number of ordinary people. %Why? 
--> 






```{r child = here::here("00-intro-adlaw.md")}
```



## Outline of the book

How, if at all, should scholars incorporate mass engagement into models of bureaucratic policymaking? 

I take up a part of this question in each of the following chapters. 
In Chapters \@ref(whymail)-\@ref(ej), I develop and test theories about the roles of individuals, organizations, coalitions, and social movements in bureaucratic policymaking.  Chapter \@ref(policy) concludes with remarks about the implications for my analysis for ongoing debates over potential reforms to the policy process.  

Each chabter draws on different kinds of literature to better understand bureaucratic policymaking. I address literatures on interest groups, lobbying, and social movements.  Chapter \@ref(whymail) integrates literature on interest-group mobilization and bureaucratic politics to understand why public pressure campaigns target agencies in the first place. Chapter \@ref(influence) focuses squarely on the classic bureaucratic politics question of interest group influence in policymaking but expanded to account for public pressure campaigns. Chapter \@ref(ej) bringing in literature on social movement pressure to show that pressure campaigns are more than a lobbying tactic; they are also an institutionalized form of contentious politics over the distribution of governmental power. 



```{r child = here::here("outline.md")}
```

