## Results: Lobbying Success {#influence-results}

This section leverages a random sample of agency rules for which I have hand-coded nearly all public comments. The first subsection presents estimates of the direct relationship between public pressure and lobbying success (Table \@ref(tab:mc-success)). The next subsection presents results of mediation analysis, assessing the support from members of Congress as a mediator for the success of public pressure campaigns (Tables \@ref(tab:model-oversight)). The third subsection presents estimates of factors affecting within-organization levels of lobbying success using a difference-in-difference design (Table \@ref(tab:mo-success-did)).

### Coalition-level Lobbying Success

Table \@ref(tab:mc-success) presents results estimating coalition-level lobbying success as a function of public pressure, coalition size, coalition type, whether the coalition supports the proposed rule, and whether there is an opposing coalition, as described in Equation \@ref(eq:success).

Models 1 and 2 use a binary measure of public pressure---did the coalition sponsor a public pressure campaign or not?  Models 2-6 use continuous measures of public pressure. Models 3 and 4 use the logged number of mass comments, reflecting the intuition that one additional comment matters more for smaller campaigns. Models 5 and 6 include both linear and quadratic terms for the number of comments to allow for a wider array of possible non-linear relationships. 

I use two related measures of coalition type. Models 1, 3, and 5 use my classification of coalitions as primarily public or private interests. Private interest is the omitted category, so coefficients are estimates of the difference in lobbying success for public interest coalitions compared to private interest coalitions. Models 2, 4, and 6 use a related, more objective measure: whether most coalition members are businesses or trade associations.

All models include fixed effects for agency and president to allow for differing average levels of lobbying success at different agencies and political conditions.<!--^[The Appendix includes a parallel set of models with random effects accounting for different levels of responsiveness to public comments in different agencies and administrations. The main results are similar]. 
<!-- TODO president interaction models in appendix
To account for partisan asymmetry in mobilizing groups, I also estimate a term for the interaction between the president and coalition type.  Bush-era rules are dropped from these models for simplicity. -->
These models include coalitions of 1 (organizations lobbying alone), but excluding them yields similar results, except that coalition size has a much weaker correlation with lobbying success. 

<!-- TODO ELLIE: "Is your design more likely to capture support for the rule? Rather than successful change given the difficulty/method of measuring change? "-->

```{r coef_map}
# load coef map 
source(here::here("code", "coef_map.R"))
```

```{r mc-success}
#mc-success

# coalition success with agency and president FE
mc1 <- feols(coalition_success ~ 
          campaign_*coalition_type + 
          # campaign_*coalition_business_ +
          # log(comments + 1)*coalition_type
          # log(comments + 1)*coalition_business_ + 
          # comments * coalition_type + 
          # comments^2 * coalition_type +
          # comments^2 * coalition_business +
          coalition_ + log(coalition_size) + #  coalition_size^2 + 
          Coalition_Position + 
          # comment_length + 
          coalition_unopposed
          # Agency and president FE 
          | agency + president, #+ president, 
        data = coalitions_coded)

mc2 <- feols(coalition_success ~ 
          #campaign_*coalition_type + # m1
          campaign_*coalition_business_ + # m2
          # log(comments + 1)*coalition_type # m3
          # log(comments + 1)*coalition_business_ + # m4
          # comments + comments^2 + coalition_type + #m5
          # comments + comments^2 + coalition_business_ + #m6
          coalition_ + log(coalition_size) + #  coalition_size^2 + 
          Coalition_Position + 
          # comment_length + 
          coalition_unopposed
          # Agency and president FE 
          | agency + president, #+ president, 
        data = coalitions_coded)

mc3 <- feols(coalition_success ~ 
          #campaign_*coalition_type + # m1
          # campaign_*coalition_business_ + # m2
          log(comments + 1)*coalition_type + # m3
          # log(comments + 1)*coalition_business_ + # m4
          # comments + comments^2 + coalition_type + #m5
          # comments + comments^2 + coalition_business_ + #m6
          coalition_ + log(coalition_size) + #  coalition_size^2 + 
          Coalition_Position + 
          # comment_length + 
          coalition_unopposed
          # Agency and president FE 
          | agency + president,# + president, 
        data = coalitions_coded)

mc4 <- feols(coalition_success ~ 
          #campaign_*coalition_type + # m1
          #campaign_*coalition_business_ + # m2
          # log(comments + 1)*coalition_type + # m3
          log(comments + 1)*coalition_business_ + # m4
          # comments + comments^2 + coalition_type + #m5
          # comments + comments^2 + coalition_business_ + #m6
          coalition_ + log(coalition_size) + #  coalition_size^2 + 
          Coalition_Position + 
          # comment_length + 
          coalition_unopposed
          # Agency and president FE 
          | agency + president,# + president, 
        data = coalitions_coded)

mc5 <- feols(coalition_success ~ 
          # campaign_*coalition_type + # m1
          # campaign_*coalition_business_ + # m2
          # log(comments + 1)*coalition_type + # m3
          # log(comments + 1)*coalition_business_ + # m4
          comments100k + comments100k^2 + coalition_type + #m5
          # comments + comments^2 + coalition_business_ + #m6
          coalition_ + log(coalition_size) + #  coalition_size^2 + 
          Coalition_Position + 
          # comment_length + 
          coalition_unopposed
          # Agency and president FE 
          | agency + president, 
        data = coalitions_coded)

mc6 <- feols(coalition_success ~ 
          #campaign_*coalition_type + # m1
          # campaign_*coalition_business_ + # m2
          # log(comments + 1)*coalition_type + # m3
          # log(comments + 1)*coalition_business_ + # m4
          # comments + comments^2 + coalition_type + #m5
          comments100k + comments100k^2 + coalition_business_ + #m6
          coalition_ + log(coalition_size) + #  coalition_size^2 + 
          Coalition_Position + 
          # comment_length + 
          coalition_unopposed
          # Agency and president FE 
          | agency + president, 
        data = coalitions_coded)

modelsFE <- list(mc1, mc2, mc3, mc4, mc5, mc6)

# paper table fixest
modelsummary::modelsummary( modelsFE, 
                            stars = TRUE, 
                            #coef_map =
                            coef_rename =  cm,
                            gof_omit = "R2 .*|IC",
                          add_rows = rowsFE, 
                          title = "OLS Models of Coalition-Level Lobbying Success",
                          notes = "") %>% 
  kable2(file = "mc-success")
```


Table \@ref(tab:mc-success) shows that the main effect of public pressure campaigns, $\beta_1$, in Model 1 is `r mc1$coefficients[1] %>% round(2)` (S.E. = `r mc1$se[1] %>% round(2)`) on the five-point scale of lobbying success. Because these models include interactions with coalition type, the main effect is the estimated effect for the omitted category. In Model 1, this is the effect of a pressure campaign for a private interest group coalition. For public interest groups, the estimate is $\beta_1 + \beta_6$ = `r (mc1$coefficients[1] + mc1$coefficients[7]) %>% round(2)`, reflecting large negative interaction between indicators for public interest coalitions and pressure campaigns (*Pressure Campaign × Public*).  Estimates are inconsistent across specifications.  

Models 3-6 use continuous measures of the scale of public pressure campaigns. Estimates are inconsistent across specifications, but Models 5 and 6 suggest that the relationship is initially negative and then positive for very large campaigns (the combined effect of the linear and quadratic terms is negative until approximately one million comments). One possible explanation for this result is that only very large campaigns create meaningful information about public demands. In sum, there is little evidence that pressure campaigns (either public or private) increase lobbying success, but there is strong evidence that public interest campaigns are much less successful than private interest campaigns. <!--If anything, there may be an overall negative relationship between campaigns that organize a large number of people and lobbying success.-->



The other strongest predictor of lobbying success across all models is whether the organization *supports the rule*. In Model 1, coalitions supporting the proposed rule change had an average success `r mc1$coefficients[5] %>% round(2)` points greater than those that opposed the rule (S.E. = `r mc1$se[5] %>% round(2)`) on the five-point lobbying success scale. This estimate is fairly consistent across specifications in Models 1-6.  This correlation likely reflects a combination of several related dynamics. First, final rules are often published without change from the draft rule. Organizations that support the new proposed rule are thus likely to "succeed" when the status quo (that is, the status quo set in the proposed rule) prevails. Second, organizations that support a proposed rule are necessarily aligned with agency officials' preferred policy direction. If agency officials change the final rule to further change policy in their preferred direction, such changes often align with organizations that supported the rule. Likewise, if commenters are aligned with agency officials, their suggestions may be more likely to be adopted, even if those suggestions do not exactly push policy further in the same direction. Finally, by selecting proposed rules that had a final rule rather than being withdrawn, this sample is missing some lobbying success by organizations that requested a proposed rule be withdrawn. 

In line with previous research, *coalition size* (the number of distinct organizations in a coalition) is correlated with lobbying success [@Yackee2006JOP; @Nelson2012]. This is notable because this sample includes rules with much more public attention and many more public comments than those used in previous studies. There is at least some evidence that these findings hold in much more salient and contentious policy fights. <!--Also, in line with previous research, there is evidence that coalitions are more successful when they lobby *unopposed*. This is notable because very few coalitions did not face opposition in this disproportionately contentious sample of agency rules. When they did, they were approximately `r mc1$coefficients[6] %>% round(2)` points more successful (estimates are fairly consistent across specifications in models 1-6). -->

The limited size of this sample means that we lack statistical power to have confidence that the estimates for many of the other variables differ from 0. Unlike previous studies on less contentious samples of rules [@Yackee2006JOP], I find no relationship between business-dominated coalitions (*business coalition*) and lobbying success. 


<!--
The main coefficient of interest (the estimated relationship between the number of comments and lobbying success) is negative across model specifications, suggesting the larger pressure campaigns are less likely to win. 



-->

As this sample consists disproportionately of draft rules that received an unusual number of comments, these results are largely based on the variation within high-salience rulemakings.

I now turn to a key variable omitted from the models in Table \@ref(tab:mc-success): the level of attention and support from an agency's political principals---specifically, members of Congress, which may mediate the effect of public pressure campaigns. 

#### Congressional Support as a Mediator of Lobbying Success

```{r}
c <- comments_congress %>% 
  group_by(docket_id) %>% 
  count() %>% 
  full_join(rules) %>% 
  mutate(n = replace_na(n, 0)) %>%
  distinct(docket_id, n, number_of_comments_received) %>% 
  filter(number_of_comments_received > n) %>% 
  mutate(comments = number_of_comments_received - n + 1)

c2 <- c %>% filter(n > 0)

cor <- cor.test(c$comments, c$n, method = c("spearman"))
```

Hypothesis \@ref(hyp:oversight)---that the overall level of public attention to a proposed rule moderates the level of attention from members of Congress---implies a correlation between the number of comments from members of Congress and all other comments on each rule. We should assess this correlation both across all rules and rules where at least one legislator commented, making it more plausible that legislators were aware of the rulemaking and thus faced the choice of whether to comment or not. Figure \@ref(fig:congress-corr) shows both of these relationships. The dashed line shows the relationship between mass comments and comments from members of Congress for all rules. The solid line shows this relationship for rules where at least one legislator commented. The right-hand panel shows this same plot with both axes on a log scale, which allows us to better observe the relationship for rules with relatively fewer comments. There is a strong correlation between mass comments and legislator attention (Spearman's rank correlation, $\rho$ = `r cor$estimate %>% round(2)`, p-value =  `r cor$p.value %>% round(3)`). However, for reasons discussed in \@ref(oversight-hypotheses), this should not be taken as strong evidence of a causal effect. 

```{r congress-corr, fig.width=2.5, fig.height=2.5, out.width="40%", fig.cap="Correlation Between Mass Comments and Comments from Members of Congress"}
# congress-corr
cplot <- c %>% 
  #filter(n > 0) %>% 
  ggplot() + 
  aes(x = comments, y = n) +
  geom_point(alpha = .5) + 
    geom_smooth(method = "lm", linetype = 2, data = c %>% mutate(n = n+1)) + 
  geom_smooth(method = "lm", data =  c %>% filter(n > 0)) + 
  labs(x = "All Other Comments", 
       y = "Comments from\nMembers of Congress")

cplot

cplot + 
  scale_x_log10() + 
  scale_y_log10()

# glm(n ~ comments,
#     family = "poisson",
#     data = c) %>% tidy()
# 
# glm(n ~ log(comments + 1),
#     family = "poisson",
#     data = c) %>% tidy()
```

To assess congressional support as a potential mediator in the influence of public pressure campaigns on rulemaking, I estimate the average conditional marginal effect (ACME, conditional on the number of comments from Members of Congress) and average direct effect (ADE) of mass comments using mediation analysis. To do this, I estimate a model predicting the proposed mediator. Because the dependent variable (the number of supportive comments from members of Congress) is a count and the dispersion parameter is not significantly above 1, a Poisson model is most appropriate. 

The first two models in Table \@ref(tab:model-oversight) are similar to those in Table \@ref(tab:mc-success), but the dependent variable is now the mediator variable (the number of supportive members of Congress). The outcome model is the same as Model 1 in Table \@ref(tab:mc-success) but includes the proposed mediator, the number of supportive comments from members of Congress. (See Equation  \@ref(eq:mediator)).

By definition, only organizations lobbying in coalition with others have members of Congress in their coalition. Thus I exclude the "coalitions" of 1 organization and omit the indicator of whether the group is lobbying in the coalition from the model. I also subtract the number of members of Congress from the coalition size. 




```{r model-oversight, cache=FALSE}
#model-oversight

# ADJUST  COALITION SIZE SO NOT ON RIGHT AND LEFT
coalitions_codedC <- coalitions_coded %>% mutate(coalition_size = coalition_size - coalition_congress)

# original model, dropping na congress obs
mc1 <- fixest::feols(coalition_success ~ 
          campaign_*coalition_type + 
          log(coalition_size) +
          Coalition_Position + 
          coalition_unopposed 
          # Agency and president FE 
          | agency + president, 
          data = coalitions_codedC %>% 
            filter(coalition_,
                   !is.na(coalition_congress) ) )


# full model
mc1_congress <- fixest::feols(coalition_success ~ 
          campaign_*coalition_type + 
          log(coalition_size) +
          Coalition_Position + 
          coalition_unopposed + 
            coalition_congress# Agency and president FE 
          | agency + president, 
               data = coalitions_codedC%>% 
            filter(coalition_) )

# model predicting mediator
mc_congress_ols <- fixest::feols(coalition_congress +1 ~ 
          campaign_*coalition_type +
            log(coalition_size) +
          Coalition_Position + 
          coalition_unopposed# Agency and president FE 
          | agency + president, 
               data = coalitions_codedC%>% 
            filter(coalition_,
                   !is.na(coalition_success) ) )

# poisson model with dummies
mc_congress_pois_dummy <- glm(coalition_congress + 1 ~ 
          campaign_*coalition_type + 
          coalition_ + 
            log(coalition_size) +
          Coalition_Position + 
          coalition_unopposed + 
            agency + 
            president, 
               family = "poisson",
               data = coalitions_codedC%>% filter(coalition_,
                   !is.na(coalition_success) ))

#library(AER)
#dispersiontest(mc_congress_pois)
               
# poisson model with FE
mc_congress_pois <- feglm(coalition_congress + 1 ~ 
          campaign_*coalition_type + 
          log(coalition_size) +
          Coalition_Position + 
          coalition_unopposed
          # Agency and president FE 
          | agency + president, 
               family = "poisson",
               data = coalitions_codedC %>% filter(coalition_,
                   !is.na(coalition_success) ))

# calculate number of members opposed to coalition
coalitions_codedC %<>% 
  ungroup() %>% 
  group_by(president, docket_id) %>% 
  # total on rule 
  mutate(congress_total = sum(coalition_congress)) %>%
  # total with shared position
  group_by(president, docket_id, Coalition_Position) %>% 
  mutate(coalition_congress_position = sum(coalition_congress),
         # total with opposed position 
         coalition_congress_opposed = congress_total - coalition_congress_position) %>%
  ungroup()

# coalitions_coded %>% select(docket_id, coalition, congress_total, coalition_congress_position, coalition_congress_opposed)

# OLS model with FE predicting opposing
mc_congress_ols_warning <- feols(coalition_congress_opposed + 1 ~ 
          campaign_*coalition_type + 
          log(coalition_size) +
          Coalition_Position
          #coalition_unopposed
          # Agency and president FE 
          | agency + president, 
               data = coalitions_codedC %>% filter(coalition_,
                   !is.na(coalition_success) ))

# poisson model with FE predicting opposing
mc_congress_pois_warning <- feglm(coalition_congress_opposed + 1  ~ 
          campaign_*coalition_type + 
          log(coalition_size) +
          Coalition_Position
          #coalition_unopposed
          # Agency and president FE 
          | agency + president, 
               family = "poisson",
               data = coalitions_codedC %>% filter(coalition_,
                   !is.na(coalition_success) ))



mediator <- list(# 'Fire alarm/Beacon Mediator Model (OLS)' = mc_congress_ols, 
                  'Fire alarm/Beacon Mediator Model (Poisson)' = mc_congress_pois, 
#                  'Warning Sign Mediator Model (OLS)' = mc_congress_ols_warning, 
                  'Warning Sign Mediator Model (Poisson)' = mc_congress_pois_warning, 
                  "Outcome Model (OLS)" = mc1_congress )

rowsMediation <- tibble(
  term = c("Dependent Variable"),
#  `Fire alarm/Beacon Mediator Model (OLS)` = c("Members of Congress in Coalition"), 
  `Fire alarm/Beacon Mediator Model (Poisson)` =c("Members of Congress in Coalition"), 
#  `Warning sign Mediator Model (OLS)` = c("Members of Congress Oposing Coalition "), 
  `Warning sign Mediator Model (Poisson)` =c("Members of Congress Opposing Coalition"), 
  `Outcome Model (OLS)`  = c("Lobbying Success"), 
)

attr(rowsMediation, 'position') <- c(0)

modelsummary(mediator, 
             stars = TRUE, 
             add_rows = rowsMediation,
             #gof_omit = ".*",
             coef_rename = cm,
             title = "Regression Models of Congressional Support and Lobbying Success for Mediation Analysis") %>% 
  kable2(file = "model-oversight")
```


The results shown in Table \@ref(tab:mc-success) do not offer much support for hypotheses \@ref(hyp:beacon)---that pressure campaigns attract support from legislators---or \@ref(hyp:warning)---that they reduce legislator opposition. If \@ref(hyp:beacon) were correct, pressure campaigns should be correlated with the number of supportive letters from members of Congress (the DV in the first column). While the effects are in the expected direction, the coefficient on *Pressure Campaign* in the "Fire alarm"/"Beacon” Mediator model is not significantly different from 0 at the .05 level. If \@ref(hyp:warning) were correct, pressure campaigns should be negatively correlated with the number of opposing comments from members of Congress (the DV in the second column). The coefficient on *Pressure Campaign* in the "Warning Sign" Mediator model is also not significantly different from 0. 

There is some evidence for relationships other than those hypothesized. Public interest coalitions may be more likely to receive support and less likely to be opposed by members of Congress, all else equal. Public interest coalitions have `r round(mc_congress_pois$coefficients[2], 2)` more supportive comments from members of Congress and have `r round(mc_congress_pois_warning$coefficients[2], 2)*-1` fewer comments opposing them. 

Because members of Congress are overall more likely to oppose proposed changes than organizations and pressure campaigns (see Figure \@ref(fig:coded-support)), there is a negative relationship between supporting a proposed rule and the number of comments from members of Congress in one's coalition. Likewise, there is a positive relationship between supporting a proposed rule and the number of members of Congress opposing one's coalition. 

The outcome model results (the third column in Table \@ref(tab:mc-success)) are similar to the results of Model 1 in Table \@ref(tab:mc-success), despite dropping organizations lobbying alone. Again, the strongest predictor of lobbying success is supporting the direction of policy change. Adding congressional support to the model improves the model fit over Model 1 in Table \@ref(tab:mc-success) (comparing R-squared and log-likelihood). The number of supportive comments from members of Congress is associated with a `r mc1_congress$coefficients[5] %>% round(2)` point difference in lobbying success (S.E. = `r mc1_congress$se[5] %>% round(2)`). <!--This is a statistically significant and somewhat substantial increase on the 5-point scale of lobbying success. This strong relationship between congressional support and lobbying success and lobbying success (controlling for other factors, including support for the proposed rule) is the most notable result from Table \@ref(tab:mc-success).
-->


```{r mediation, warning=FALSE, message=FALSE}
# model predicting DV
model.m <- lm(coalition_congress ~ campaign_ + 
                #comment_length + 
                coalition_type +  
                log(coalition_size),# + 
                #coalition_unopposed, 
              data = coalitions_codedC %>% filter(coalition_, !is.na(coalition_success))) 

model.m.pois <- glm(coalition_congress ~ campaign_ + 
                #comment_length + 
                coalition_type +  
                log(coalition_size), #+ 
                #coalition_unopposed,
               family = "poisson",
              data = coalitions_codedC %>% filter(coalition_, !is.na(coalition_success))) 


# model predicting DV
model.y <- lm(coalition_success ~ campaign_ + 
                coalition_congress +
                  #comment_length + 
                coalition_type +  
                log(coalition_size), #+ 
                #coalition_unopposed, 
              data = coalitions_codedC %>% filter(coalition_)) 
models <- list(model.m, model.y)
# modelsummary(models)

# Mediation 
med.cont <- mediate(model.m, model.y,
                    sims=1000, 
                    treat = "campaign_", 
                    mediator = "coalition_congress")
#med.cont %<>% tidy()

#tidy(med.cont) %>% kable3(caption = "Mediation Analysis with Pressure Campaign as Treatment and Congressional Support as Mediator for Lobbying Success"))

```

<!--For mediation analysis, I use the OLS version of both mediator and outcome models.-->

While there is some evidence that public pressure campaigns affect the proposed mediator---support from members of Congress---there is little evidence for the main relationship of interest. Given this, the proposed mediation analysis does not offer much additional leverage on the hypotheses.
The average effect of a public pressure campaign on lobbying success, conditional on letters from members of Congress (the ACME), is `r round(med.cont$d.avg, 2)` on the 5-point scale, with a p-value of `r round(med.cont$d0.p, 4)`. 
<!--
The Average Direct Effect (ADE) of a public pressure campaign on lobbying success is `r round(med.cont$z0, 2)`, with a p-value of `r round(med.cont$z0.p, 4)`.

<!--The Total Effect (ADE + ACME) of a public pressure campaign is `r round(med.cont$tau.coef, 2)`, with a p value of `r round(med.cont$tau.p, 2)`. `r round(med.cont$n0, 2)` of this is mediated through mobilizing congressional attention (p-value = `r round(med.cont$n0.p, 2)`).-->


### Difference in Differences in Organization-level Lobbying Success

<!--TODO ELLIE "Say more about what you mean here? The organizations know they're going to lose, and they're trying to do something to signal to their members that they tried? Or do the organizations think they're going to lose but launch a pressure campaign as a hail mary? "-->

I now turn from assessing variation *across coalitions* to variation *within organizations* as they lobby in multiple coalitions across policies and over time.
Estimates in Models 1 of Table \@ref(tab:mo-success-did) show the results of estimating Equation \@ref(eq:dnd). <!--These results suggest that the organizations were less successful when they mobilized more comments, more successful when they supported the rule, and less successful under President Trump than President Obama. -->
Models 2 presents results from a similar model with fixed effects for each rule rather than for each agency. Model 3 includes indicator variables for each president interacted with the main variables of interest (whether an organization lobbies with a coalition that mobilizes public pressure and whether an organization lobbies with a public or private interest coalition). 


```{r mo-success-did}
# mo-success-did
mo1 = feols(success ~ campaign_*coalition_type + 
                   coalition_ + 
                   log(coalition_size) + 
              coalition_congress+
                   Position 
                 # fixed effects
                 | org_name + agency + president,
               data = comments_coded %>% 
  filter(comment_type == "Org") %>% 
  distinct(agency, org_name, docket_id, success, Position, coalition_congress, coalition_type,
           coalition_, coalition_size, coalition_comments, president, campaign_) )

mo2 = feols(success ~ campaign_*coalition_type + 
                   coalition_ + 
                   log(coalition_size) + 
              coalition_congress+
                   Position 
                 # fixed effects - docket instead of agency and president 
                 | org_name + docket_id,
               data = comments_coded %>% 
  filter(comment_type == "Org") %>% 
  distinct(agency, org_name, docket_id, success, Position, coalition_congress, coalition_type,
           coalition_, coalition_size, coalition_comments, president, campaign_) )

# president dummy 3- way interaction 
mo3 = feols(success ~ campaign_*president*coalition_type + 
                   coalition_ + 
                   log(coalition_size) + 
              coalition_congress+
                   Position 
                 # fixed effects
                 | org_name + agency,
               data = comments_coded %>% 
  filter(comment_type == "Org") %>% 
  distinct(agency, org_name, docket_id, success, Position, coalition_type, coalition_congress,
           coalition_, coalition_size, coalition_comments, president, campaign_) )

models_o_success <- list(mo1, mo2, mo3)

modelsummary(models_o_success, 
             stars = T, 
             add_rows = success_rows3,
             coef_rename = cm,
             title = "Difference-in-Difference Model of Lobbying Success Within Organizations") %>% kable2(file = "mo-success-did")
```

Like the coalition-level models in Table \@ref(tab:mc-success), organizations were more likely to get their desired result when they supported the proposed rule. The effect sizes are smaller in the difference-in-difference specification but significantly different from zero. 

The most notable result from models 1 and 2 is the negative correlation between lobbying success and the number of pressure campaigns organized by public interest groups (*Pressure Campaign × Public*). As discussed above, it is likely due to public interest campaigns "going down fighting," whereas private interest campaigns are more likely to only lobby when they think they anticipate it increasing their chances of winning. Unlike private interest campaigns, some public interest campaigns are not trying to influence policy but instead build power for future policy fights (see Chapter \@ref(whymail). The fact that organizations are more likely to get the outcome they seek when they support the draft rule makes sense because the agency is more likely to be sympathetic to their requests.


The model in the third column of Table \@ref(tab:mo-success-did) clarifies that the large negative correlation between public interest campaigns and lobbying success is a result of losing campaigns during the Trump administration. Model 3 includes the president as an indicator variable interacted with the indicators for the pressure campaign and coalition type (whereas Models 1 and 2 estimate fixed effects for each president). First, it shows that the average organization was less likely to see its desired policy changes under President<!--s G.W. Bush and--> Trump than under President Obama. This is likely due to asymmetry in organizations in this sample of high-salience rules, with far more organizations on the political left than the political right in this sample of rules. Supporting this conclusion, there is a positive interaction between the indicators for a pressure campaign and for President Trump (*Pressure Campaign × Trump*) for private interest groups (the omitted category), but a very large negative relationship for public interest group campaigns under President Trump (*Pressure Campaign × Public × Trump*). 

<!--
The estimate from Model 3 for organizations lobbying in private coalitions (the omitted category of coalition type) opting to lobbying with a pressure campaign during the Trump administration (compared to the Obama administration) is  `r round(mo3$coefficients[1]+mo3$coefficients[3]+mo3$coefficients[10], 2)` ($\beta_1+\beta_3 +\beta_{10}$). When we add the coefficients for the terms that account for an organization's coalition being led by public interest groups---all of which are negative---the estimated effect of opting to campaign on lobbying success `r round(mo3$coefficients[1]+mo3$coefficients[3]+mo3$coefficients[10], 2)` ($\beta_1+\beta_3 +\beta_{10}$). This evidence of responsiveness to private but not public interest pressure campaigns aligns with the business-friendly image that president-Trump projected. -->


## Conclusion {#influence-conclusion}

Public pressure campaigns appear to help private interests more than public interests on average. However, this correlation could have at least two observationally equivalent causes. First, my theory predicts a strong selection effect. By nature, public interest groups need to build grassroots power, contact lists, and a donor base to persist to fight the next day. Unlike businesses, public interest organizations thus have incentives to launch pressure campaigns even when they have little hope of influencing policy. Second, pressure campaigns from business groups are rarer and perhaps more surprising. Formal models of bureaucratic policymaking suggest that policymakers should be most affected by surprising information. Policymakers may be more likely to expect campaigns from public interest groups and even have prior beliefs that the public is on their side. A large segment of the public voicing support for a cause that bureaucrats perceived as narrow may be more likely to make them question or revise their prior beliefs about the public or the politics of their proposed policy.

Even among private interest groups and businesses, however, 
I find mixed evidence that public pressure campaigns increase lobbying success.  There are several possible explanations for this result. For example, it may be that agencies may not be persuaded by political information, either because of the institutions for dealing with public input or decisionmakers' biases. Alternatively, the relatively small sample may simply lack the power to reliably estimate small effects. 

<!--TODO ELLIE: "Or that they only launch mass comment campaigns on the "difficult" issues when they think simple technocratic comments from the org won't be enough.  Or they know that opposition is/will be mobilized, etc.  "-->

I do find evidence that public pressure campaigns coalitions mobilize support from members of Congress and reduce overt opposition by members of Congress. However, legislators disproportionately align with private interest coalitions (i.e., coalitions led by business interests), not the public interest coalitions that run most public pressure campaigns.