# Data

In order to examine whether environmental justice advocates or public pressure campaigns shape the discourse around policies,
I use the text of draft rules, public comments, and final rules retrieved from regulations.gov. I select rulemaking documents from agencies that pubished at least one rule explicitly addressing Environmental Justice fron 1992 through 2020. This yields 30348 rulemaking dockets from 44 agencies.  

```{r data, fig.cap = "Number of Rules where Environmental Justice Appears in the Record (Left) and Number of Comments per Notice or Proposed Rule (Right).", out.height = NULL, out.width = "49%", fig.show = "hold"}


```



64,128,301 public comments were recieved on these dockets, of which 24,360 unique comments (excluding duplicates) use the phrase “environmental justice”.

Despite E.O. 12868, most rules do not address environmental justice. 
Figure
\@ref(fig:ej) 



```{r ej, fig.cap = "Number of Rules where Environmental Justice Appears in the Record (Left) and Number of Comments per Notice or Proposed Rule (Right).", out.height = NULL, out.width = "49%", fig.show = "hold"}

knitr::include_graphics(here::here("Figs", "eandj-hist.pdf") ) #  

knitr::include_graphics(here::here("Figs", "eandj-comments.pdf") ) # 
```




Figure \@ref(fig:ej)
shows that the number of rules and comments increasing over time. This
may reflect increased salience of this concept, but it may primarily be
the result of the increasing prevalence of searchable texts. Similarly,
the increased number of rules where comments mention environmental
justice may reflect growth in the movement but also may reflect more
overall comments as technology has made commenting easier. Testing the
hypotheses that comments raising environmental justice concerns are
related to specific rules where environmental justice is addressed in
the final but not in the draft requires rule-specific analysis.

What we can say from Figure \@ref(fig:ej) is that each year, more final rules directly address
environmental justice when their draft did not. Additionally, there are
many rules where environmental justice is mentioned in the public
comments and not in the draft. Recently, there are also many rules where
environmental justice is raised in the comments but does not make it
into the final draft.^[Note that, because not all comments are machine-readable, this is an
    underestimate of the number of comments mentioning environmental
    justice, so we cannot conclude that before 2010, rules were
    mentioning environmental justice when the comments had not.
    Additionally, this does not include comments like those of the
    Bishops who raise justice issues but do not use the phrase
    "environmental justice."]

## Second-order Representation

Before analysis of whether comments matter, I briefly describe who these
commenters are. This is what @Seifter2016UCLA calls "second-order"
representation. It is insufficient to know which groups participate. We
also need to know who these groups represent.

I investigate who is raising environmental justice concerns in two ways.
First, I identify the top organizational commenters such as tribes,
businesses, and nonprofits that are using environmental justice language
and investigate who these groups represent. Second, for comments where a
citizen signed their name, I compare surnames to their racial and ethnic
identity propensities with respect to the U.S. census. Together these
two pieces of information allow me to comment on "second order"
representation, i.e. not just the extent to which public comments relate
to government policy, but the extent to which public comments are
representative of the public and of the groups they claim to represent.

Table: (\#tab:orgs) Organizations mobilizing mass comment campaigns mentioning "environmental justice"

       Organization                           Comments   Rules
  ---- -------------------------------------- ---------- -------
     1 Earthjustice                           1114782    28
     2 Natural Resources Defense Council      340554     8
     3 Sierra Club                            349841     5
     4 Alliance for Climate Protection        253867     5
     5 WE ACT for Environmental Justice       2402       3
     6 CREDO                                  112879     2
     7 Union of Concerned Scientists          43559      2
     8 Earthworks                             308        2
     9 Communities for a Better Environment   21         2
    10 Southern Company                       8          2
    11 Move On                                165948     1
    12 Care2                                  70450      1
    13 The Pew Charitable Trusts              63769      1
    14 Hudson-Environmental Action            35000      1
    15 Democracy for America                  4426       1


Table \@ref(tab:orgs) shows the top 15 organizational commenters who
used the phrase "environmental justice" in their comments, including all
organizations who did so on more than one rule or mobilized more than
100,000 such comments. The six organizations responsible for mobilizing
more than 100,000 comments and several others on the list are national
nonprofit advocacy groups. We Act and Communities for a Better
Environment are both more community-based groups focusing primarily on
environmental justice issues. Southern Company is the only corporation
on the list

The top mobilizer, Earthjustice, is primarily engaged in litigation on
behalf environmental causes. Their website boasts 2.2 million
supporters, but it is not clear who they are or if they play any role in
the advocacy strategy. A search on the website returns 360 results for
\"Environmental Justice,\" with the top results from staff biographies
who work on more local or targeted work such as environmental conditions
for the incarcerated, but the environmental justice language used on the
main page is relatively mild. For example, "We are fighting for a future
where children can breathe clean air, no matter where they live"
[@Earthjustice2017]. The website does contain Spanish language content.

The Natural Resources Defense Council is similar to Earthjustice--a
national nonprofit funded by donations and focused on litigation--but
they also lobby. CREDO Action and MoveOn are more generic progressive
mobilizers who lack a systematic focus on environmental justice issues,
but occasionally leverage their very large membership lists to support
campaigns environmental justice campaigns led by others
[@MoveOn.org2017; @CREDO2017]. The Alliance for Climate Protection is a
more of an elite political group founded by former Vice President Al
Gore.

We Act and Communities for a Better Environment both have environmental
justice in their central mission statement. We Act was founded by
community leaders in Harlem, NY, to fight environmental racisms and
advocate for better air quality [@WEACT2017]. Communities for a Better
Environment has projects throughout California but is particularly
active in Oakland [@CBECAL2017CommunitiesEnvironment]. Much of the
content of their website is in both English and Spanish. Both
organizations focus primarily on "low-income communities of color" and
thus frame their work with respect to race and class. While both
organizations participated in national policymaking We Act is more
focused on communities in Harlem and New York whereas Communities for a
Better Environment casts a wider frame: \"CBE's vision of environmental
justice is global--that's why the organization continues to participate
in such international efforts as the Indigenous Environmental Network
and the Global Week of Action for Climate Justice\" [@CBECAL2017].

The Southern Company comments are too few to count as mass mobilization.
Companies do sometimes fund mobilization campaigns, but all of 8 of
these comments were submitted by the Southern Company. Interestingly,
the company repeatedly raises research into environmental justice
concerns in order to frame these issues as a legitimate but unresolved
scientific debate that is not yet conclusive enough to base regulations
on: \"People with lower SES are exposed to almost an order of magnitude
more traffic near their homes (Reynolds et al., 2001), and live closer
to large industrial sites and are exposed to more industrial air
pollution (Jerrett et al., 2001). Legitimate health concerns must be
addressed. But adopting standards with a scientific basis so uncertain
that health improvement cannot be assured is not sound public health
policy.\" Like many companies they claim to represent their customers as
\"electric generating companies and their customers are expected to bear
much of the burden\" of regulations [@Hobson2004].

With respect to second-order representation, it appears that the groups
most often using the language of environmental justice may do so
sincerely but do not themselves represent affected communities. Several
groups representing local communities and led by community leaders have
participated, but not nearly as often or with the same intensity as the
"big greens." This highlights the importance of resources as a condition
for mobilizing. Not all groups who may benefit from political
information are able to leverage it because they lack the resources to
invest in a campaign. However, it may be the case that smaller, more
member-driven groups join coalitions with groups with more resources who
mobilize on their behalf. More work is needed to identify coalitions to
assess this possibility.

Finally, a third class of commenter raises environmental justice issues
as a way to re-frame them as ongoing debates and thus undermine their
urgency. I call this reason for engaging as "breaking a perceived
consensus." In a way, the fact that an energy company felt compelled to
acknowledge and question environmental justice concerns suggests their
importance for policy outcomes.

Next, I attempt to estimate the racial distribution of those who comment
using environmental justice language. This can only be done for
individuals who commented separately from mobilizing organizations and
signed their full name on their comment. Figure
\@ref(fig:ejcommentsbyrace) shows two ways of estimating the racial
distribution of commenters who raise "environmental justice" concerns in
their comments. Both methods use the reported racial identities
associated with surnames as recorded in the 2010 census^[I recode "Hispanic" as "Latinx" in both cases because the
    prediction method assumes a forced choice that includes "Hispanic"
    as a primary racial category] 
and are
based on a limited sample of 327 commenters who signed their name with a
surname matching census records. The first is based on the proportion of
people with a given surname that identified as belonging to each racial
category (from this limited set of options). The estimated proportion of
each race for this sample is simply the average of proportions
identified with each surname. This is likely the most accurate way to
represent the racial distribution of a set of surnames, but it does not
assign specific individuals to racial categories. The second method
does. It predicts the race of each individual in the sample based on
their surname given the distribution of racial categories reported by
people with that surname and the proportion of each race in the U.S.
population. Thus, while a surname may be more common among people who
identify as black rather than as white, there may still be more White
people with that surname and this method would predict that the person
is White. For this reason, the portion of individuals predicted to be
White (right) is higher than in the probabilistic distribution (left).


```{r ejcommentsbyrace, fig.cap = "Probabilistic (Left) and Predicted (Right) Race from Census Surnames", out.height = NULL, out.width = "49%", fig.show = "hold"}

knitr::include_graphics(here::here("Figs", "race-prob.pdf"))

knitr::include_graphics(here::here("Figs", "race-pred.pdf"))
```


Compared to estimates from the 2010 census, this sample of commenters
appears to be disproportionately Black and less than proportionately
Latinx or Asian, with just slightly fewer Whites relative to the
national population. This makes sense given that environmental justice
theorizing and activism have been led by African American's
[@Bullard1993].

Figure \@ref(fig:ejwordsbyrace) shows the most common words used in comments
with respect to the predicted race of each commenter in the sample. As
there are very few predicted non-White commenters in the sample, it is
unwise to infer too much from this figure.

   


```{r ejwordsbyrace, fig.cap = 'Most frequent words used in comments mentioning "environmental justice" by predicted race (From Left: White, Latinx, Black)', out.height = NULL, out.width = "32%", fig.show = "hold"}

knitr::include_graphics(here::here("Figs", "ej-white-words.pdf"))

knitr::include_graphics(here::here("Figs", "ej-latinx-words.pdf"))

knitr::include_graphics(here::here("Figs", "ej-black-words.pdf"))
```

