---
# rmarkdown::render("02-pressure/whyMail.Rmd")
# output_dir: "../docs"  # to push
output_dir: "docs"  # to push
title: Why Do Agencies (Sometimes) Get So Much Mail?
subtitle: Public Pressure Campaigns and Bureaucratic Policymaking
author: Devin Judge-Lord

# author:
# - name: Devin Judge-Lord
#   affiliation: 
#   footnote: "University of Wisconsin-Madison, [judgelord@wisc.edu](mailto:judgelord@wisc.edu). Slides and the most recent draft are available at <https://judgelord.github.io/research/whymail>"
date: |
   `r Sys.Date()` Draft. Slides and the most recent draft are available at [judgelord.github.io](https://judgelord.github.io/research/whymail/) 
abstract: | 
  `r readLines(here::here("02-pressure/abstract.txt"))`

documentclass: memoir
#documentclass: article
classoption: oneside
always_allow_html: true
fontsize: 12pt
geometry: "left = 1.25in, right = 1.25in, top = 1.25in, bottom = 1.25in"
bibliography: '`r here::here("assets/dissertation.bib")`'
biblio-style: '`r here::here("assets/apsr.bst")`'
link-citations: yes
citecolor: black
urlcolor: blue
language:
  ui:
    chapter_name: "Chapter "
# endnotes: true # CHANGE THIS BEFORE SUBMISSION
frontpage: true
spacing: onehalfspacing
# github-repo: https://github.com/judgelord/dissertation
# description: ""
keywords: Interest groups, rulemaking, lobbying, bureaucratic politics

output:
    bookdown::pdf_document2:
      #template: '../assets/article-template.tex' # redirect to assets 
      keep_tex: true
      latex_engine: xelatex
      citation_package: natbib
      toc: false
      fig_caption: true
      fig.topcaption: true
      fig.width: 7
      includes:
        in_header: "../assets/preamble-memoir.tex"
---

```{r global.options, include=FALSE, cache=FALSE}
# load defaults
source(here::here("code", "setup.R"))

# overide defaults
knitr::opts_chunk$set(cache = FALSE,
                      fig.path = "../figs/")
```

<!--
\centerline{\textbf{\underline{NOTE TO READER}}}

\thispagestyle{empty}

The following chapter is part of a dissertation exploring the effects of public pressure campaigns on agency rulemaking, a technocratic policy process where “public participation” is usually limited to sophisticated lobbying but occasionally includes millions of people mobilized by public pressure campaigns. Public comment periods on proposed policies purport to provide democratic accountability. Yet theories of bureaucratic policymaking largely ignore the occasional bursts of civic engagement that generate the vast majority of public comments on proposed rules. To fill this gap, I build and test theories about the role of public pressure in policymaking. I collect and analyze millions of public comments to develop the first systematic measures of civic engagement and influence in bureaucratic policymaking. The outline of the dissertation is as follows:  

{rchild = here::here("outline.md")}



\newpage
-->

\setcounter{page}{1}

\OnehalfSpacing


```{r child = here::here("02-pressure/01-why-intro.Rmd")}
```

```{r child = here::here("02-pressure/02-why-mobilize.Rmd")}
```

```{r child = here::here("02-pressure/03-why-methods.Rmd")}
```

```{r child = here::here("02-pressure/04-why-results.Rmd")}
```



\newpage

```{r child = here::here("99-appendix.Rmd")}
```

\begin{figure}
    \caption{Unique or Partially Unique Comments by Sentiment Score (Sample of 2018 Rules)}
    \label{fig:sentiment-2018}
    \centering
    \includegraphics[width = 7in]{../Figs/sent-2018ATF-2018-0001.png}
    \includegraphics[width = 7in]{../Figs/sent-2018ATF-2018-0002.png}
    \includegraphics[width = 7in]{../Figs/sent-2018BIS-2018-0006.png}
    \includegraphics[width = 7in]{../Figs/sent-2018BLM-2018-0001.png}
    \includegraphics[width = 7in]{../Figs/sent-2018BSEE-2018-0002.png}
    \includegraphics[width = 7in]{../Figs/sent-2018CEQ-2018-0001.png}
\end{figure}

\begin{figure}
    \caption{Unique or Partially Unique Comments by Sentiment Score (Sample of 2016 Rules)}
    \label{fig:sentiment-2016}
    \centering
    \includegraphics[width = 7in]{../Figs/sent-2016BLM-2016-0001.png}
    \includegraphics[width = 7in]{../Figs/sent-2016CMS-2016-0116.png}
    \includegraphics[width = 7in]{../Figs/sent-2016EPA-HQ-OAR-2016-0004.png}
    \includegraphics[width = 7in]{../Figs/sent-2016FWS-HQ-ES-2016-0010.png}
    \includegraphics[width = 7in]{../Figs/sent-2016HHS-OS-2016-0014.png}
    \includegraphics[width = 7in]{../Figs/sent-2016NOAA-2005-0226.png}
\end{figure}

\clearpage

## Descriptive Data About Public Comments


```{r comments-from, fig.cap="Sources of Comments Posted to regulations.gov"}
knitr::include_graphics(here::here("Figs", "comments-from.pdf"))
```

\begin{figure}[p!]
    \centering
        \caption{Major and Non-major Rules on regulations.gov}
    \includegraphics[width = 7in]{../Figs/major-comments-density-1.png}
    \label{fig:rules-major}
\end{figure}

\begin{figure}[p!]
    \centering
        \caption{Rules on regulations.gov by Unified Agenda Priority Level}
    \includegraphics[width = 7in]{../Figs/priority-comment-density-1.png}
    \label{fig:rules-priority}
\end{figure}



\clearpage 


